This section integrates the within-country evidence (Sections~\ref{sec:test_h} and~\ref{sec:test_i}) and the across-country evidence (Section~\ref{sec:across}) into a joint reading. We organize the discussion around five questions: (i) what bounds the within-country regressions place on the elasticity of substitution $\sigma$ between regulated and unregulated suppliers; (ii) what mechanisms are consistent with the within-country null; (iii) what mechanisms are consistent with the across-country null; (iv) which mechanisms operate at both margins jointly; and (v) selection and external validity for the joint pattern.

\subsection{Bounds on the elasticity of substitution}\label{sec:bounds}

The regression coefficients in Sections~\ref{sec:test_h} and~\ref{sec:test_i} can be mapped, under explicit CES and pass-through assumptions, to bounds on the elasticity of substitution $\sigma$. We make the assumptions explicit and report two bounds: a preferred conservative bound under partial pass-through, and a tighter benchmark under full pass-through. The conservative bound is the headline; the tight bound is the upper-bound-on-precision case.

\paragraph{Mapping coefficients to $\sigma$.} Consider a CES nest where buyer $b$ allocates expenditure across suppliers $j$ in NACE 4-digit category $n$, with elasticity $\sigma$ across suppliers. For small price changes,
\[
    \mathrm{d}\log s_{j} \;=\; (1 - \sigma)\,\bigl(\mathrm{d}\log p_{j} \;-\; \mathrm{d}\log P_n\bigr),
    \qquad
    \mathrm{d}\log P_n \;=\; \sum_{k} s_k\,\mathrm{d}\log p_k.
\]
If only supplier $j^*$'s price changes, $\mathrm{d}\log p_{j^*} - \mathrm{d}\log P_n = (1 - s_{j^*})\,\mathrm{d}\log p_{j^*}$, and
\[
    \mathrm{d} s_{j^*} \;\approx\; s_{j^*}\,(1 - \sigma)\,(1 - s_{j^*})\,\mathrm{d}\log p_{j^*}.
\]
Under full pass-through, $\mathrm{d}\log p_{j^*} \approx \text{firm cost share}_{j^*}$. The Test~H regression coefficient on $\text{firm cost share}_{j^*} \times \mathbf{1}[\text{Post}]$, with $\text{share top}$ in percentage points, satisfies
\begin{equation}
    \beta \;\approx\; 100 \cdot \rho \cdot s_{j^*}\,(1 - \sigma)\,(1 - s_{j^*}),
    \qquad
    \sigma \;=\; 1 \;-\; \frac{\beta}{100\,\rho\,s_{j^*}\,(1 - s_{j^*})},
    \label{eq:sigma_within}
\end{equation}
where $\rho \in [0, 1]$ is the pass-through coefficient from supplier marginal cost to invoice price.

\paragraph{Within-NACE-4d bound.} Plugging in the most-favorable subset of Test~H (Q4 of the buyer's pre-shock NACE-4d expenditure share, where the supplier-level price change converts to the largest dollar shock at the buyer's total-cost level): $\widehat{\beta} = +0.03$, 95\% CI $\approx [-2.7, +2.8]$ percentage points per unit of cost-share intensity. With $s_{j^*} = 0.30$ (a representative pre-shock share for the most-exposed ETS supplier in cells with $\geq 2$ suppliers), the implied $\sigma$ depends on the assumed pass-through coefficient $\rho$ from supplier marginal cost to invoice price.

Our preferred bound uses $\rho = 0.5$, which we view as the conservative reading: it is consistent with our own OLS pass-through estimate (S6 with sector trends, $+0.07$ insignificant) and serves as a lower bound on the CMdG-tight Phase~2 coefficient after sector trends ($+0.094$). This gives
\[
    \sigma \;\in\; [0.74,\; 1.26]\quad(95\%\text{ CI}),\qquad
    \widehat{\sigma}\;\approx\;1.0.
\]
Under full pass-through $\rho = 1$ --- the maximum-precision case, but harder to defend given our own OLS pass-through evidence --- the bound tightens to $\sigma \in [0.87, 1.13]$. We report the latter as an upper-bound-on-precision benchmark, not as the headline. The full sample ($\widehat{\beta} = +1.34$, s.e.\ $0.96$ on the firm-cost-share regressor) gives $\sigma \in [0.69, 1.06]$ at $\rho = 0.5$ and $\sigma \in [0.85, 1.03]$ at $\rho = 1$.

The implication is sharp under either pass-through assumption. We rule out, at conventional confidence levels, elasticities of substitution between regulated and unregulated suppliers within the same NACE 4-digit \emph{above $\sim$1.3} under our preferred conservative pass-through and \emph{above $\sim$1.1} under full pass-through. The point estimates cluster around $\sigma = 1$, the Cobb--Douglas benchmark, in which buyers' relative quantity demand still moves one-for-one with relative prices but expenditure shares do not. The bounds are consistent with $\sigma$ in a narrow neighborhood of unity. Trade-elasticity magnitudes commonly identified in import-substitution work \citep[e.g.,][with $\sigma \approx 4$]{peter2023} are outside our 95\% confidence interval under both pass-through assumptions.

\paragraph{Across-NACE-4d bound.} The Test~I.3 binary regulated $\times$ \textit{Post} coefficient is $\widehat{\beta} = -0.003$ (s.e.\ $0.009$, p = 0.76), with the outcome a buyer-category expenditure share. Under the across-category CES analog of \eqref{eq:sigma_within} with $\sigma_{\text{cat}}$ as the across-category elasticity, an average regulated-category pre-shock share $s_{\text{reg}} \approx 0.05$, and an average post-2015 regulated-vs-unregulated log-price differential of $\Delta \log p \approx 0.10$ (the average of CMdG-tight Phase~2 and Phase~4 coefficients with sector trends, \S\ref{sec:passthrough}),
\[
    \sigma_{\text{cat}} \;\in\; [0.5,\; 5.0]\quad(95\%\text{ CI}),\qquad
    \widehat{\sigma}_{\text{cat}}\;\approx\;1.05.
\]
This is a wider bound than the within-NACE-4d bound because the price increment is more dispersed and the average within-buyer regulated-category share is smaller. The point estimate is again near $\sigma = 1$. The bound is consistent with sector-input elasticities typically estimated in macro production-network work \citep[e.g.,][]{baqaee2019} and rules out only large elasticities.

\paragraph{Joint reading.} Our two reallocation margins jointly identify an elasticity of substitution centered close to 1.0, with the within-NACE-4d bound the tighter of the two. Under our preferred pass-through assumption ($\rho = 0.5$), elasticities between roughly $0.74$ and $1.26$ are within the within-NACE-4d 95\% CI; under full pass-through, the CI tightens to $[0.87, 1.13]$. Across categories, elasticities up to $\sim$5 are within the 95\% CI. We cannot separate elasticities below 1 (\ie complementarity) from elasticities exactly at 1; we can rule out elasticities at the magnitudes typically estimated in import-substitution work for differentiated intermediates.

\subsection{Mechanisms for the within-country null}\label{sec:within_mechanisms}

Our within-country finding of $\sigma \approx 1$ does not point uniquely at a single mechanism. Five candidate explanations are observationally consistent with the pattern; they are not mutually exclusive, and we cannot separately identify them with current data. We list them roughly in order of how directly the data speak, with one caveat: explanation (1) below --- the most natural first guess, that the shock is too small at the typical buyer --- is the explanation we have the \emph{least} direct support for, because the right-tail evidence cuts against it. We list it first because addressing it is the precondition for treating the rest seriously.

\paragraph{(1) The shock is small at the typical buyer --- but the right-tail data argue against this as the primary explanation.} A natural first instinct is that the population-level $\sigma \approx 1$ estimate reflects a too-small shock. The pair-shock-total distribution at the buyer-total-cost level is heavy-tailed: the population p99 is $\approx 39\%$ (with cement at p99 $\approx 67\%$), while the population p50 is $\approx 0.002\%$. Most buyers face essentially no shock to substitute against. If the elasticity were truly larger than 1 but only detectable at high shock magnitudes --- a heterogeneous-$\sigma$-by-shock-size story --- the test specification would still capture it at the right tail.

The right-tail evidence cuts against the shock-magnitude explanation. The relevant external benchmark is \citet{peter2023}, who identify $\sigma \approx 2.5$--$4$ at the 5-digit ASICC level off the post-1991 Indian intermediate-input tariff liberalization, where average tariff cuts on regulated input categories were on the order of $\sim$30 percentage points. Our right-tail buyer cells face price shocks at the same scale or larger: the population p99 of buyer-cell pair-exposure corresponds to a per-supplier price shock under full pass-through of $\approx 39\%$ of cell-level cost, and the cement p99 reaches $\approx 67\%$. In signal-to-noise terms, the cement-buyer pair-shock-total at p90 is $8.80\%$ of total inputs against a cement-buyer cost-share standard deviation of $13.0\%$ (signal-to-noise $\approx 0.68\sigma$) --- meaningful and near the conventional detectability threshold; non-cement sectors are below this threshold. If a heterogeneous-$\sigma$-by-shock-size story were correct, the right tail of our exposure distribution is where the elasticity would identify, and our specifications target it directly.

We test the right tail through the Q4 pair-exposure split: the coefficient is $+29.0$ pp per unit of pair-exposure (s.e.\ $20.7$, $p = 0.16$), versus a pooled coefficient of $-16.7$ (s.e.\ $17.4$). Two readings of this contrast are informative for the shock-magnitude story:

\begin{itemize}
    \item In $\beta$ space, the \emph{direction} is wrong for a heterogeneous-$\sigma$ explanation on the pair-exposure regressor. A model in which the elasticity rises with shock magnitude predicts $\widehat{\beta}_{Q4} < \widehat{\beta}_{\text{pooled}}$ (i.e., more negative, indicating larger substitution at the right tail); we observe $\widehat{\beta}_{Q4} > \widehat{\beta}_{\text{pooled}}$ (more positive, the opposite direction). The cross-quartile difference $\widehat{\beta}_{Q4} - \widehat{\beta}_{\text{pooled}} = +45.7$ is suggestive but not significant ($z \approx 1.7$ under a conservative independence approximation, $p \approx 0.09$); the point of this contrast is the sign, not the magnitude.\footnote{Translating pair-exposure $\widehat{\beta}$ directly into $\sigma$ through the firm-cost-share CES mapping in equation~\eqref{eq:sigma_within} would mis-state the result, because the pair-exposure regressor is the product $\text{firm cost share} \times \text{pre-share}$, so its CES coefficient is rescaled by $1/\overline{\text{pre share}}$. With $\overline{\text{pre share}}_{Q4}$ on the order of $0.05$--$0.10$, $\widehat{\beta}_{Q4} = +29$ maps to $\widehat{\sigma}_{Q4} \approx 0.86$--$0.93$, not to a structurally implausible negative value. We avoid the pair-exposure $\sigma$-mapping in this paper because it requires an additional moment ($\overline{\text{pre share}}_{Q4}$) that the firm-cost-share regressor's mapping does not.}
    \item The same conclusion holds in $\sigma$ space when we use the firm-cost-share regressor's quartile splits by buyer's pre-shock NACE 4-digit expenditure share (Table~\ref{tab:test_h_main}, panel ``Quartile splits''). Q1 (lightly-affected, where the supplier-level price change converts to the smallest dollar shock at the buyer's total-cost level) gives $\widehat{\sigma}_{Q1} \approx 1.81$ with a wide 95\% CI of $[0.55, 3.07]$ at $\rho = 1$; Q4 (heavily-affected) gives $\widehat{\sigma}_{Q4} \approx 1.00$ with a tight 95\% CI of $[0.87, 1.13]$. A heterogeneous-$\sigma$-by-shock-size story predicts $\widehat{\sigma}_{Q4} > \widehat{\sigma}_{Q1}$; the data point in the opposite direction. The cross-quartile difference is not statistically significant, but it is the heavier-shock subsample, not the lighter, that pins $\sigma$ tightly at the Cobb--Douglas point.
\end{itemize}

The honest interpretation is that the shock-magnitude explanation is the one with the \emph{least} direct support among the five we list. We list it first only because it is the first explanation a referee or reader is likely to propose, and because addressing it directly is necessary to defend the population-level $\sigma \approx 1$ estimate as informative. The data favor the alternative explanations (relational capital, regulated-alternative saturation, partial pass-through, buyer-side absorption) over the small-shock story. We cannot rule out a smoother non-linearity that would only become detectable at carbon prices several multiples above the realized 2022 EUA.

\paragraph{(2) Relational capital is high in Belgian B2B.} Belgian firm-to-firm relationships are unusually persistent. Among all active pairs in 2005--2022, pairs older than five years are 18\% of pairs but $\sim$79\% of total trade. Within total-duration cohorts, mean log corrected-sales rises monotonically with pair age, and the break-up hazard falls from $\sim$46\% at age 0 to $\sim$14\% at age 18. This is a relational-capital pattern of the kind documented in \citet{baqaee2019} for production networks more broadly: the buyer-supplier match accumulates value over time (specifications, joint testing, customized billing and logistics), and switching costs grow with pair age. Substitution that requires breaking such pairs would be costly even at non-trivial relative-price increments. We do not separately identify the magnitude of these switching costs; the relational-capital pattern is consistent with $\sigma \approx 1$ within the existing pair distribution but cannot pin down whether $\sigma$ is small in a hypothetical pool of identical varieties.

\paragraph{(3) Regulated and unregulated alternatives often coincide within the same NACE 4-digit.} The within-NACE-4d substitution test requires that buyers can reach an unregulated alternative within the same supplier sector. In Belgium, ETS coverage is concentrated in heavy industries where most large suppliers in the same NACE 4-digit are themselves ETS-regulated. In NACE 19 (refined petroleum), the ETS share of revenue is essentially 100\%; in NACE 24 (basic metals), $\sim$90\%; in NACE 23 (cement and other non-metallic minerals), $\sim$58--80\%. A buyer who substitutes from an ETS cement producer to ``the alternative'' supplier in the same 4-digit category is, in many cases, substituting toward another ETS-regulated firm that absorbs the same cost shock. The relative-price gap inside the regulated NACE 4-digit is therefore much smaller than the gross supplier-level price increment, even under full pass-through. This narrows the substitution that the buyer would observe and is consistent with the within-NACE-4d null. The across-NACE-4d test (Section~\ref{sec:test_i}) is robust to this concern by construction --- it compares regulated to unregulated categories rather than within-category alternatives --- and also returns a null.

\paragraph{(4) Pass-through of carbon costs into supplier invoice prices is incomplete.} The bounds in \S\ref{sec:bounds} treat $\rho \in [0.5, 1]$ as the pass-through range. The CMdG-tight Phase~2 coefficient with sector-specific linear trends is $+0.094$ (a 9.4\% relative-PPI gap accumulated over a five-year window). If marginal-cost pass-through is partial --- because suppliers absorb part of the shock or because pass-through is delayed --- the buyer-side relative-price signal is dampened. Our $\sigma$ bound widens but does not become uninformative under partial pass-through; it does, however, reduce the buyer's incentive to substitute. The OLS pass-through evidence in \S\ref{sec:passthrough} (S6 with sector trends, $+0.07$ insignificant) and \citet{martin2014}'s Belgian firm-level finding of $+0.14$ insignificant on PRODCOM unit prices both suggest that within-sector firm-level pass-through is heterogeneous and not always close to unity.

\paragraph{(5) Buyer-side pass-through dampens the substitution incentive.} The Belgian buyers in our sample sell on to their own customers, who may absorb part of the carbon-driven cost increase. A buyer that can pass the shock downstream has a smaller incentive to bear the search and switching costs of finding an alternative supplier. We do not measure buyer-side pass-through directly; the across-country customs evidence in Section~\ref{sec:across} is consistent with buyer-side absorption rather than substitution toward foreign suppliers, but absorption alone is not a clean test of mechanism (5). We list it for completeness.

\paragraph{Mechanisms we cannot separate.} (1)--(2) and (3)--(4) operate jointly: a small shock at the typical buyer compounds with high relational capital, limited unregulated alternatives within the supplier sector, and partial pass-through that dampens the relative-price signal. We do not have an exclusion restriction that separates these mechanisms cleanly. The most we can say is that the within-country null at $\sigma \approx 1$ is consistent with all five operating in the same direction and that the data do not single out any one as dominant.

\subsection{Mechanisms for the across-country null}

Section~\ref{sec:across:bevfrance} lays out three working hypotheses for why the Belgian customs panel returns small or wrong-signed coefficients on the CMdG specification, in contrast to the French Phase~3 share coefficient of $+0.121$***. We summarize them here.

\paragraph{(A) Intra-EU substitution as the reaction margin.} The most plausible substantive explanation. Belgian buyers post-2005 may have shifted regulated-product sourcing toward EU-domestic suppliers (also subject to the EU ETS, but cheaper to reach logistically and free of currency or customs friction) rather than toward non-ETS countries. The negative Phase~2 and Phase~3 coefficients on Belgium are consistent with this: the regulated $\times$ non-ETS share fell because Belgian buyers consolidated to EU sources for regulated inputs. France, with lower intra-EU trade integration, has more headroom to substitute toward non-EU sources at the margin.

\paragraph{(B) Pre-existing chemicals saturation.} The Antwerp chemicals cluster competes with Chinese, Indian, and Saudi chemical exporters on global markets and was already heavily integrated with non-ETS sources before 2005. Belgian buyers of regulated chemical inputs may have sourced as much as they were ever going to from non-ETS countries pre-treatment; further shifts post-treatment hit a saturation ceiling. France's chemical sector is smaller in relative terms, leaving more room for post-treatment reallocation.

\paragraph{(C) Sample-size attenuation in column~(5).} Methodological rather than substantive. With $\sim$3{,}000--5{,}000 Belgian firms versus France's 27{,}000, the firm $\times$ product $\times$ country fixed-effect block is sparser in Belgium, and the country $\times$ year fixed effects absorb a larger share of identifying variation. Cross-column comparison shows that columns without country $\times$ year fixed effects deliver share coefficients closer to $\pm 0.005$ --- still small in absolute terms, but at least directionally consistent with France in some cells. Column~(5) absorbs whatever Belgian-leakage signal exists into the FE structure.

We cannot separately identify these channels with the current data. (A) and (B) are substantive (Belgium is genuinely different from France); (C) is methodological (Belgium is in principle identifiable like France, but with weaker power). Distinguishing them would require either pooling Belgium with other small EU economies or a within-firm dose-response design on PRODCOM unit-price data, both of which we leave for future work.

\subsection{Mechanisms operating jointly at both margins}

Three of the within-country mechanisms (\S\ref{sec:within_mechanisms}) and two of the across-country mechanisms have the same operative content and reinforce each other when read across both margins:

\begin{itemize}
    \item \emph{Saturation of the unregulated alternative.} Within-country: regulated NACE 4-digit categories (refining, basic metals, much of cement and chemicals) are heavily ETS-saturated, narrowing the within-sector relative-price gap. Across-country: the Antwerp chemicals cluster was already saturated with non-ETS exporters before 2005, narrowing the cross-border relative-price gap. Both imply that the price differential a buyer would observe in response to the EU ETS shock is smaller than gross supplier-level pass-through would suggest, and dampens the substitution incentive at both margins.

    \item \emph{Pass-through partial on the buyer side.} Within-country: buyer-side pass-through onto downstream customers absorbs part of the cost shock; the buyer's incentive to substitute is reduced. Across-country: the same buyer-side absorption logic rationalises why we observe small or wrong-signed cross-border share coefficients. Buyer-side pass-through ties the two margins together: a Belgian buyer that absorbs the cost shock through its own pricing has reduced incentive to pursue \emph{either} domestic or foreign substitutes.

    \item \emph{Intra-EU integration.} For across-country, intra-EU integration is the reaction margin: Belgian buyers consolidate to EU regulated sources rather than pivot to non-EU. For within-country, the same intra-EU integration channel explains why the within-NACE-4d ``unregulated alternative'' is itself often regulated --- because EU regulation extends to the entire intra-EU supply, the within-country and across-country margins share an underlying structural reason for being small.
\end{itemize}

The cross-margin coherence of these mechanisms is itself informative: if the within-country and across-country results came from independent measurement-error realisations, we would not expect the same set of mechanisms to rationalise both. The fact that one consistent narrative spans both margins increases our confidence that the joint null reflects a structural feature of the Belgian economy rather than two coincidental nulls.

\subsection{Selection}

\paragraph{Within-country.} The pre-shock cost-share intensity in equation~\eqref{eq:fcs} is computed from data ending in 2014 or 2016, so the regressor cannot mechanically incorporate post-2015 outcomes. The universe of buyers in the across-category test (\S\ref{sec:test_i}) excludes buyers with no positive pre-shock spending in the category. This exclusion is needed to define the buyer-category cell, but it means the test has no power against substitution that operates by a buyer adding a new category to its input bill. We do not have a direct test for this margin and flag it as a gap in coverage rather than an estimated null.

\paragraph{Across-country.} The customs panel pre-period (2000--2003) shows a non-zero pre-trend on the probability margin (Figure~\ref{fig:cmdg_event_study}, Panel B), so identification under parallel-trends is questionable for the extensive-margin Panel B coefficient; we report Panel A as the cleaner result. The capital-goods filter uses the HS~2007 (H3) $\to$ BEC concordance instead of HS~2002 (H2), which differs marginally from CMdG's exact filter; the difference is unlikely to drive the Belgium-vs-France divergence given its order of magnitude. Three contaminated VAT hashes in NACE~20 and~24 (post-2020 EUTL artifacts) are not dropped from the customs panel, since the contamination is in EUTL emissions data, not customs imports.

\subsection{External validity}

Belgium is a small open economy and the Belgian ETS is a small subset of the EU-wide system. Four external validity concerns deserve flagging:

\begin{enumerate}
    \item \emph{ETS firms in Belgium are large and established.} The 281 EUTL installations are concentrated in established firms (steel, cement, refining, primary chemicals), all of which were operating throughout the sample window. The composition of the regulated set is older and more capital-intensive than the average EU ETS sector. A test in a setting with more entry of new regulated firms --- or more exit of old ones --- might find different reallocation magnitudes.

    \item \emph{The 2017--2022 EUA price path is one realization of one policy.} Our identification leans on the post-2017 MSR-driven price rise. Different prices, different time horizons, or different cap stringencies might produce different reallocation responses. We do not extrapolate.

    \item \emph{Belgium's B2B network is unusually well-measured.} The near-universal NBB B2B records make this a high-power setting for observational within-country substitution tests; settings without similar firm-to-firm coverage may not be able to replicate the within-country specification at all. The applicability of our within-country null to settings without similar data is unclear.

    \item \emph{Cross-country heterogeneity is large.} The Belgium-vs-France comparison on the customs panel (\S\ref{sec:across:bevfrance}) shows that cross-border leakage on the same EU ETS regime differs by roughly a factor of fifty across two large EU economies. This is itself a feature of the data: our null on Belgian customs imports is consistent with a Belgian-specific industrial composition (intra-EU integration density, Antwerp chemicals saturation) that does not generalize to other EU member states. Drawing EU-wide conclusions from any single-country leakage estimate is therefore hazardous; the joint within-and-across-country measurement is informative for Belgium specifically and offers a benchmark against which similar measurements in other EU countries can be compared.
\end{enumerate}

We do not claim that our results generalize across economies, and we are explicit that the Belgium-vs-France divergence on the cross-border margin is itself the strongest illustration of cross-country heterogeneity. We claim that, for Belgian buyers facing the post-2017 EU ETS price increment, on the four margins we observe (two within-country and two outcome panels of the across-country test), both leakage channels are quantitatively small, the within-country elasticity of substitution is tightly identified at the Cobb-Douglas benchmark, and the cross-border share coefficient is two orders of magnitude smaller than the corresponding French estimate.
