Carbon leakage --- the reallocation of regulated-good production toward unregulated jurisdictions or unregulated suppliers in response to a unilateral carbon price --- has been the central empirical premise behind three of the most consequential design features of unilateral climate policy. Free allowance allocation, which forgoes more than half of EU ETS auction revenue, presumes that regulated firms would lose customers to unregulated alternatives if they passed full carbon costs forward. Output-based rebates and product-specific subsidies presume similar customer reallocation at the product level. The Carbon Border Adjustment Mechanism (CBAM), phased in by the EU from 2023 and under active consideration in the UK, the US, and Canada, presumes large cross-border substitution toward non-ETS sources of carbon-intensive goods. All three policies cost or distort something --- forgone auction revenue, sectoral disaggregation requirements, administrative costs, trade-policy risk --- and all three are justified by an assumed empirical magnitude of leakage that has, to date, been measured on only one of its theoretically distinct margins.

This paper measures the two margins of EU ETS leakage \emph{jointly} on the same economy under the same identification window. The leakage literature has long distinguished the two margins conceptually: domestic across-firm reallocation, in which buyers within the regulating jurisdiction shift purchases from regulated to unregulated domestic suppliers; and international cross-border reallocation, in which buyers shift purchases toward less-regulated foreign sources. Empirically, the literature has measured the two margins separately, with quite different evidentiary bases. The cross-border margin has been studied via trade flows in \citet{aichelefelbermayr2015}, \citet{naegelezaklan2019}, \citet{satodechezlepretre2015}, and most recently \citet{CosterMejeanDiGiovanni2024} (CMdG hereafter) on French firm-level customs data, who find a $\sim$12 percentage-point Phase~3 reallocation of regulated imports toward non-ETS sources. The within-country across-firm margin has been inferred only indirectly from the fact that regulated EU ETS firms reduced emissions without contracting output \citep{martin2014,colmeretal2023,dechezlepretreetal2023,kanzig2023unequal}; it has not been measured directly, because no public dataset combines firm-level emission regulation with full-network firm-to-firm transactions. The same economy under the same policy regime delivers, in this paper, the first joint within-and-across-country measurement.

Our setting is Belgium under the post-2017 EU Emissions Trading System price rise. The setting has three properties that make joint measurement feasible. First, the National Bank of Belgium (NBB) maintains a near-universal panel of business-to-business invoices linked by VAT identifier; we observe the full domestic supplier composition of essentially every Belgian buyer, which is what enables direct measurement of the within-country across-firm margin. Second, the NBB and Eurostat jointly maintain a near-universal customs panel covering Belgian goods imports at the firm $\times$ HS6 product $\times$ source country $\times$ year level, which is the analog of the data \citet{CosterMejeanDiGiovanni2024} use for France --- enabling a clean replication on the cross-border margin. Third, the EU ETS supplies a pre-specified policy event with a well-understood structural break: the 2015 Market Stability Reserve reform triggered a roughly tenfold rise in EUA prices over 2017--2022, generating a Phase~IV cost shock that, by every external benchmark, dwarfs the variation that prior leakage studies have used for identification (Section~\ref{sec:msr_identification}).

\paragraph{Findings.} We document four results.

\begin{itemize}
    \item \textbf{Pass-through is real.} On a 2005--2019 monthly NACE 4-digit PPI panel, regressing log price changes on the \citet{kanzig2023unequal} structural carbon-policy shock interacted with sector-level pre-shock carbon-cost intensity returns a peak coefficient of $+4.08$ (s.e.\ $0.64$) at $h = 12$ months. A regulated-vs-unregulated event study with sector-specific linear trends recovers Phase~2 and Phase~4 differential PPI gaps of $+0.094$ and $+0.113$. The price signal that would cause reallocation is operative on Belgian regulated suppliers (\S\ref{sec:passthrough}).

    \item \textbf{Within-country across-firm leakage is small.} On the Belgian B2B panel 2005--2022, we test reallocation at two margins: across suppliers within the same NACE 4-digit (\S\ref{sec:test_h}) and across NACE 4-digit input categories (\S\ref{sec:test_i}). Mapped into a CES nest using the empirical within-cell ETS-saturation moment $E[s_{j^*}(1 - s_{E_n})]$, the within-NACE-4d full-sample bound is $\sigma \in [+0.05, +1.17]$ at $\rho = 0.5$ and $\sigma \in [+0.52, +1.08]$ at $\rho = 1$, with point estimate at the Cobb-Douglas benchmark $\widehat{\sigma} \approx 1.00$. The across-category margin gives a wider but consistent bound, $\sigma_{\text{cat}} \in [0.5, 5.0]$ centered at $1.05$. The reduced-form regression coefficients underlying these bounds are precisely zero, and the CI widths are governed by the within-cell ETS saturation: the sales-weighted ETS share within Test~H cells is $\approx 0.91$, so the ``unregulated alternative'' to the most-exposed regulated supplier is itself usually regulated.

    \item \textbf{Across-country cross-border leakage is small and Belgium $\neq$ France.} Replicating \citet{CosterMejeanDiGiovanni2024} on Belgian customs imports 2000--2019 (\S\ref{sec:across}), the Phase~3 share coefficient is $-0.0024$**, two orders of magnitude smaller than France's $+0.121$*** and pointing in the opposite direction. Phase~2 is $-0.0037$*** versus France's $+0.110$***. The result is robust across four control-group choices and six fixed-effect specifications. No specification recovers CMdG-style positive coefficients. The Belgium-vs-France divergence on the same EU ETS regime is itself an empirical fact: cross-border leakage is heterogeneous across EU member states by roughly a factor of fifty, and country-level industrial composition (Antwerp chemicals saturation, intra-EU integration density) plausibly explains a substantial share of the heterogeneity.

    \item \textbf{Joint reading.} Both margins are small in Belgium under the post-2017 EU ETS regime. We are not aware of a prior paper that measures both directly on the same economy under the same identifying event. The result is empirically tight enough to challenge the assumed magnitudes of leakage that motivate free allocation (within-country) and CBAM (cross-border) policies, and the cross-country comparison with France suggests that any such challenge is contingent on the importing economy's industrial and trade structure rather than universal.
\end{itemize}

\paragraph{What we do and do not measure.} We measure two margins of leakage directly: across-firm domestic reallocation in B2B transactions, and across-country cross-border reallocation in customs imports. We do not measure three margins on which leakage could in principle operate: (i) production relocation, in which the regulated firm itself moves operations outside the regulated jurisdiction; (ii) services trade, since the customs panel covers goods only; and (iii) imports post-2019, since the customs panel ends at a 2020 administrative break that the NBB has not retroactively reconciled. We also do not estimate a structural model that decomposes aggregate emission responses into abatement and reallocation channels --- that is the question of a complementary structural paper (\S\ref{sec:policy} discusses what our reduced-form numbers imply for it). The contribution of this paper is empirical: putting direct measurement on the two leakage margins where prior work has been indirect (within-country) or one-sided (across-country with a single benchmark).

\paragraph{Five mechanisms consistent with the joint null.} The joint pattern is consistent with several non-mutually-exclusive mechanisms (\S\ref{sec:discussion}): (i) shock magnitudes are small at the typical pair, but the right tail of pair-exposure cuts against this as the primary explanation, since the most-affected buyer cells fail to deliver the substitution-by-shock-size that the heterogeneous-$\sigma$ story would require; (ii) Belgian B2B exhibits substantial relational capital --- pairs older than five years are 18\% of pairs but $\sim$79\% of total trade --- that raises switching costs in the within-country test; (iii) within heavily ETS-regulated NACE 4-digit categories, the ``unregulated alternative'' is itself often ETS-regulated, narrowing the within-country relative-price gap; (iv) for the across-country margin, intra-EU substitution is the natural reaction to a within-EU policy: Belgian buyers consolidate to EU-domestic regulated sources rather than pivot to non-ETS countries, which is consistent with the \emph{negative} signs we recover on the customs panel; (v) the Antwerp chemicals cluster was already heavily integrated with non-ETS exporters before 2005, leaving limited headroom for further substitution.

\paragraph{Related literature.} We connect to four strands.

\emph{Cross-border leakage.} \citet{aichelefelbermayr2015}, \citet{naegelezaklan2019}, and \citet{satodechezlepretre2015} measure cross-border leakage via aggregate trade flows; \citet{CosterMejeanDiGiovanni2024} provides the firm-level analog on French customs data. Our cross-border result is a direct replication of CMdG on Belgian data; the divergence is the Belgian fact that the literature has not yet documented.

\emph{Within-country EU ETS firm-level effects.} \citet{martin2014}, \citet{dechezlepretreetal2023}, \citet{colmeretal2023}, and \citet{kanzig2023unequal} document that EU ETS firms reduced emissions without contracting output. The standard reading of this pattern --- that within-country leakage must therefore be small --- has not been tested directly on across-firm B2B substitution. Our within-country result confirms that reading.

\emph{Production-network calibration.} \citet{baqaee2019}, \citet{king2019}, and \citet{aghion2024} provide the theoretical machinery for translating firm-level reallocation responses into aggregate-emissions effects of carbon policy. The elasticity of substitution $\sigma$ is the central calibration target for this work; our $\widehat{\sigma} = 1.00$ on Belgian B2B is direct firm-level evidence on this parameter, replacing what has previously been free or borrowed from trade-microdata estimates.

\emph{Demand elasticity in environmental settings.} \citet{Hsiao2026} estimates own-price palm-oil demand elasticities of $0.7$ to $0.9$ via an AIDS specification with weather IVs and emphasizes that low substitution \emph{strengthens} the case for trade-policy intervention because it limits leakage to unregulated markets. The structural role of his demand elasticity in the palm-oil setting is analogous to the role of $\sigma$ in our production-network setting: a low estimated elasticity translates a reduced-form null into a positive structural argument about the effectiveness of unilateral environmental policy.

The remainder of the paper proceeds as follows. Section~\ref{sec:data} describes the EU ETS, the MSR-driven identifying event, and the three Belgian micro-datasets we use. Section~\ref{sec:passthrough} presents the pass-through evidence that anchors both leakage tests. Sections~\ref{sec:test_h} and~\ref{sec:test_i} report the within-country across-supplier and across-category tests respectively; Section~\ref{sec:across} reports the across-country CMdG replication. Section~\ref{sec:discussion} discusses the joint pattern, candidate mechanisms, selection, and external validity. Section~\ref{sec:policy} draws the policy implications. Section~\ref{sec:conclusion} concludes.
