A precondition for either margin of leakage is that carbon costs reach buyers as a relative-price increase on regulated suppliers. We document this precondition on the same Belgian panel under three identification strategies and use the resulting magnitudes to anchor the within-country mapping of regression coefficients to elasticities of substitution in Section~\ref{sec:discussion} and to interpret the across-country results in Section~\ref{sec:across}.

\paragraph{Strategy 1: monthly panel local projections on the Känzig structural carbon-policy shock.} On a 2005m1--2019m12 monthly NACE 4-digit PPI panel, regressing $\log \text{PPI}_{s,m+h} - \log \text{PPI}_{s,m-1}$ on the interaction of the \citet{kanzig2023unequal} carbon-policy structural shock $\text{CPShock}_m$ with the sector's pre-shock cost-share intensity $\text{intensity}_s^{\text{base}}$, with sector and year-month fixed effects, gives an impulse response that builds gradually and peaks at $h = 12$ months: $\beta_{12} = +4.08$ (s.e.\ $0.64$, $t = 6.39$). The IRF shape (modest on impact, peak at 12 months, fade by 24 months) reproduces the aggregate-HICP IRF in \citet{kanzig2023unequal} when run through the same pipeline. For a sector with $\text{intensity}_s^{\text{base}} \approx 0.005$ and a $\pm 1$ standard-deviation monthly shock, the implied $h = 12$ PPI response is $\pm 0.6$\%.

\paragraph{Strategy 2: regulated-vs-unregulated event study at NACE 4-digit, with sector-specific linear trends.} Following \citet{colmeretal2023}, we estimate
\[
    \log \text{PPI}_{s,t} \;=\; \sum_\tau \beta_\tau\,\mathbf{1}[s \in \text{regulated}]\,\mathbf{1}[\text{year} = \tau] \;+\; \alpha_s \;+\; \delta_t \;+\; \theta_s \cdot t \;+\; \varepsilon_{s,t}
\]
on the 2001--2022 annual NACE 4-digit panel with sector-specific linear trends $\theta_s \cdot t$. Phase-aggregated coefficients (CMdG-tight treatment of seven NACE 2-digit codes, the same set as in \citet{CosterMejeanDiGiovanni2024}'s Table A.5):
\[
    \widehat{\beta}_{\text{Phase 2}} \;=\; +0.094\,(***), \qquad \widehat{\beta}_{\text{Phase 4}} \;=\; +0.113\,(**).
\]
Phase 1 and Phase 3 coefficients collapse to insignificance once sector trends are absorbed; we report Phase 2 and Phase 4 because those are the periods where regulated PPI rises differentially after netting out pre-existing sector-level dynamics.

\paragraph{Strategy 3: descriptive OLS with sector-specific trends.} The annual exposure-share elasticity is small ($+0.07$ in S6 with sector trends) and not significantly different from zero on a single-shock specification --- consistent with the literature \citep[e.g.,][]{martin2014} that finds firm-level pass-through dispersed and noisy in the cross-section. The strongest piece of identifiable evidence remains Strategy 1.

\paragraph{Anchor for the rest of the paper.} For the elasticity bounds in Section~\ref{sec:discussion} we use the regulated-vs-unregulated CMdG-tight estimate as the average post-2015 log-price differential between regulated and unregulated NACE 4-digit categories, with magnitude $\approx 0.10$ (\ie about 10 log-points cumulative over Phase 2 and Phase 4). At the right tail, sector-level pass-through is consistent with full pass-through under Strategy 1; we use $\rho = 1$ as an upper bound and $\rho = 0.5$ as a lower bound on the buyer-side relative-price signal. The pass-through evidence also speaks to the across-country test in Section~\ref{sec:across}: buyers face a price differential between regulated EU suppliers and unregulated non-EU suppliers of roughly the same order of magnitude as the within-country differential, so the across-country leakage incentive is a priori comparable.
