The joint pattern --- both within-country across-firm leakage and across-country cross-border leakage small in Belgium under the post-2017 EU ETS price increment --- has direct implications for the design of unilateral carbon-pricing protections. Free allowance allocation, output-based rebates, and the Carbon Border Adjustment Mechanism are all justified by leakage premises that our reduced-form numbers speak to directly. We discuss each in turn, then flag the three margins our empirical strategy does not bound and the implications for production-network calibrations of carbon policy.

\subsection{Free allowance allocation: within-country rationale empirically weaker}

The within-country leakage rationale for free allowance allocation rests on a high elasticity of substitution between regulated and unregulated suppliers within the regulating jurisdiction. The standard argument: if a regulated firm passes its full carbon costs forward, downstream buyers will substitute away to unregulated alternatives, the regulated firm loses market share, and the policy generates lost domestic production rather than emission reductions. Free allocation reduces the regulated firm's marginal cost of compliance and dampens this reallocation. The argument is quantitatively important: in Phase~III/IV, free allowances account for more than half of all EU ETS allowances issued, with annual auction revenue forgone in the tens of billions of euros at Phase~IV prices.

Our within-country bound is $\sigma \in [0.74, 1.26]$ at the within-NACE-4d margin under our preferred conservative pass-through assumption, and $[0.5, 5.0]$ at the across-category margin. Both intervals are centered close to Cobb-Douglas, well below the elasticities that an aggressive-leakage interpretation would require. The reduced-form coefficients are precisely zero. In the Belgian setting, the empirical premise that motivates free allocation to immobile installations --- domestic buyers will reallocate substantially toward unregulated domestic alternatives --- is not borne out in the firm-to-firm data.

This conclusion is contingent on the regulating jurisdiction. The within-country mechanism we identify in \S\ref{sec:within_mechanisms} (regulated-alternative saturation within heavy NACE 4-digit categories, dense relational capital, partial pass-through) is plausibly stronger in Belgium than in larger EU economies with more diversified within-sector supply structures. Our result is most credibly read as a bound for dense-network small open economies in which the EU ETS is concentrated in established heavy industries; it does not speak directly to economies with more entry of new regulated firms or with more diffuse regulatory coverage within sectors.

\subsection{CBAM: cross-border rationale also weaker on Belgian customs evidence}

The Carbon Border Adjustment Mechanism rests on a different empirical premise: cross-border substitution toward non-ETS sources of carbon-intensive goods. CBAM was phased in by the EU starting in 2023 and is under active consideration in the UK, the US, and Canada. The core argument: a unilateral carbon price on EU producers will cause downstream EU buyers to shift purchases of regulated goods toward non-EU origins, the EU loses regulated production while global emissions are unchanged, and the policy generates leakage rather than abatement. CBAM extends the carbon price to imports from non-ETS jurisdictions and closes this margin.

Our across-country replication of \citet{CosterMejeanDiGiovanni2024} on the Belgian customs panel returns Phase~3 coefficients of $-0.0024$**, two orders of magnitude smaller than the corresponding French coefficient of $+0.121$*** and pointing in the opposite direction. The Phase~2 coefficient is $-0.0037$***. The result is robust across four control-group choices and six fixed-effect specifications. No specification recovers CMdG-style positive coefficients. Belgian buyers did not, on the customs panel 2000--2019, shift their imports toward non-ETS sources for regulated products. The CBAM rationale, on Belgian evidence alone, is empirically weaker than the policy currently presumes.

Two important caveats. First, CMdG's France finding is very different. The Belgium-vs-France divergence is itself an empirical fact, with industrial-composition explanations (intra-EU integration density, Antwerp chemicals saturation) that we discuss in \S\ref{sec:across:bevfrance}. CBAM is an EU-wide policy; conclusions about it should weight EU-wide cross-border leakage rather than any single-country estimate. Our Belgian null is one input into that EU-wide calculation, and the Belgium-vs-France factor of fifty is the cross-country heterogeneity that EU-wide policy design must engage with. Second, our customs panel ends in 2019. Phase~IV cross-border leakage --- where the EU ETS price spiked from EUR 30 to EUR 80+ per tCO$_2$ --- could in principle activate cross-border substitution that the pre-2019 evidence does not capture. We do not measure this and treat it as an open question.

\subsection{What we do not measure}

Three margins on which leakage could in principle operate are out of scope for our empirical strategy:

\begin{itemize}
    \item \emph{Production relocation by the regulated firm itself.} We observe domestic Belgian firms only; we cannot detect a regulated installation that closes in Belgium and reopens in a non-ETS jurisdiction. Production-relocation leakage is the most prominent argument for free allocation to mobile installations (e.g., aluminum smelters, primary chemicals plants with multiple-jurisdiction footprints). Our results do not speak to it.

    \item \emph{Services trade.} The customs panel covers goods imports only. Services with significant carbon content (consultancy, engineering) are not included.

    \item \emph{Imports post-2019.} The Belgian customs panel ends at a 2020 administrative break that the NBB has not retroactively reconciled with the pre-2020 series. Phase~IV (2021+) is the highest-EUA-price phase to date, and cross-border leakage in this window may be quantitatively different from the Phase~II/III estimates we report. Extending the customs panel through Phase~IV is a natural future direction.
\end{itemize}

These three margins are jointly the ``escape valves'' that could in principle restore the leakage rationale for free allocation and CBAM even given our null on the two margins we measure. A cautious reading of our results is that, on the two margins for which Belgian micro-data deliver direct measurement, leakage is small; the leakage rationale for unilateral carbon-policy protections rests, in light of our null, on the three margins we cannot bound and on cross-country heterogeneity that future work should map.

\subsection{Implications for production-network calibrations of carbon policy}

Quantitative production-network models of carbon policy \citep[e.g.,][]{baqaee2019,king2019,aghion2024} translate firm-level reallocation responses into aggregate emissions effects of unilateral carbon pricing. A central calibration target for these models is the elasticity of substitution between regulated and unregulated suppliers --- in the within-country test, the elasticity that summarises buyer reallocation in production networks. Our within-country bound of $\sigma \in [0.74, 1.26]$ provides a direct, identification-disciplined target value for one well-measured economy.

Three implications for these models:

\begin{itemize}
    \item \emph{Calibrating $\sigma$ at unity is empirically supported.} The macro production-network literature has often used $\sigma \approx 1$ as a calibration default. Our result is direct micro-evidence that this default is well-aligned with firm-level Belgian B2B data, replacing what has previously been free or borrowed from trade-microdata estimates ($\sigma \approx 4$) that disagree with our setting.

    \item \emph{Cross-border substitution at $\sigma \approx 1$ is consistent with our customs result.} The across-country reduced-form null we recover on the Belgian customs panel implies a cross-border elasticity that, mapped through an analogous CES nest, is also small. Calibrating both within and across margins at unity (or below) yields a model in which unilateral carbon pricing operates primarily through firm-level abatement rather than reallocation, consistent with the standard reading of \citet{colmeretal2023} and \citet{kanzig2023unequal}.

    \item \emph{Cross-country heterogeneity is a first-order calibration consideration.} Calibrating an EU-wide carbon-policy model on cross-border-leakage estimates from a single large country (e.g., CMdG France) would likely overstate the aggregate-emissions effects of unilateral carbon pricing in dense-network small open economies, and understate them in larger economies with more diversified non-EU sourcing patterns. The Belgium-vs-France factor-of-fifty divergence is the empirical motivation for incorporating country-specific calibration of cross-border substitution into EU-wide structural models.
\end{itemize}

A complementary structural paper that decomposes aggregate emission responses into abatement and reallocation channels using Belgian micro-data is in progress; our reduced-form numbers in this paper provide direct moments for that decomposition.
