\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{array}
\usepackage{caption}
\usepackage{xcolor}

\newcommand{\N}{\mathcal{N}}

\title{Empirical Exercises on Reallocation:\\
\large Notes on What We've Done So Far}
\author{Working Note}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
These notes document each empirical exercise we have run to test whether
Belgian carbon pricing induced \emph{output reallocation} from dirty to clean
firms. For every exercise I define the variables, write the specification,
state the identification assumption, and report headline results.
\end{abstract}

\tableofcontents

\section{Notation used throughout}

Let $i$ index firms, $s$ index NACE 4-digit sectors (or 2-digit where stated), and $t$ index years.
\begin{itemize}
  \item $e_{i,t}$: verified CO\textsubscript{2} emissions (EUTL) in tCO\textsubscript{2}.
  \item $q_{i,t}$: real revenue, equal to nominal turnover deflated by the NACE 4-digit domestic PPI (Statbel from 2010; Eurostat chain-linked back to 2005).
  \item $Y_t = \sum_i q_{i,t}$: total real output in the sample in year $t$.
  \item $\theta_{i,t} = q_{i,t} / Y_t$: firm $i$'s share of total real output.
  \item $z_{i,t} = e_{i,t} / q_{i,t}$: firm $i$'s emission intensity (tCO\textsubscript{2} per euro of real revenue).
  \item $E_t = \sum_i e_{i,t}$: total emissions. Note the identity
  \begin{equation}
      E_t \;=\; Y_t \sum_i \theta_{i,t}\, z_{i,t}. \label{eq:identity}
  \end{equation}
  \item $\mathrm{shortage}_{i,t} = \max(e_{i,t} - \mathrm{free}_{i,t},\, 0)$, where $\mathrm{free}_{i,t}$ is freely allocated allowances.
  \item $\mathrm{EUA}_t$: annual mean EUA secondary-market price, in \euro/tCO\textsubscript{2}.
  \item $\mathrm{firm\_cost\_share}_i$: firm-level pre-MSR carbon cost share (defined in \S\ref{sec:phase4}).
  \item $\mathrm{intensity\_base}_s$: NACE 4-digit sector pre-MSR carbon cost share (same construction as \cite{phase3}).
\end{itemize}
The clean sample covers 88.4\% of Belgian ETS emissions in 2005 and ranges from 162 to 194 firms per year.

\bigskip

\section{Six-channel pairwise emission decomposition}
\label{sec:pairwise}

\textbf{Script:} \texttt{analysis/phase0\_pairwise\_decomposition.R}.

For each pair of years $(t_0, t_1)$ we decompose the total change in aggregate EUTL emissions into six exhaustive channels.

\subsection{Variables}

Primitive variables as defined in \S1 ($e_{i,t}$, $q_{i,t}$, $Y_t$, $\theta_{i,t}$, $z_{i,t}$, $E_t$). For a given pair:
\begin{itemize}
  \item \textbf{Survivors} $S$: firms with $e_{i,t} > 0$ in both $t_0$ and $t_1$, joined on firm ID (\texttt{vat}). A firm that switches NACE 2d between years is still a survivor; its $t_0$ sector is used for the between/within split.
  \item \textbf{Entrants} $N$: firms with $e_{i,t_1} > 0$ but no positive emissions in $t_0$.
  \item \textbf{Exiters} $X$: firms with $e_{i,t_0} > 0$ but no positive emissions in $t_1$.
  \item Within-survivor aggregates: $Y_{t,S} = \sum_{i \in S} q_{i,t}$, $\theta_{i,t}^S = q_{i,t}/Y_{t,S}$.
  \item Group-average intensities, reported alongside the table in tCO\textsubscript{2} per million \euro{} of real revenue: $\bar z^E = \sum_{i \in N} e_{i,t_1} / \sum_{i \in N} q_{i,t_1}$ and $\bar z^X = \sum_{i \in X} e_{i,t_0} / \sum_{i \in X} q_{i,t_0}$.
  \item \textbf{Triple-balanced panel}: the 101 firms with positive emissions in all of 2005, 2012, and 2020; reported as a separate block in the table to allow a strict same-firm comparison of the pre- and post-2012 windows. Entry and exit are zero by construction on these rows.
  \item \textbf{Three firms excluded} from rows ending in 2022 (marked $^{\ddagger}$ in the table): one NACE 24 installation (likely ArcelorMittal Gent: 4.6 Mt $\to$ 0.09 Mt over 2020--2022 while revenue grew from 3{,}399 to 6{,}476 M\euro{}) and two NACE 20 installations. All three show EUTL verified emissions and free allocation collapsing to near-zero in 2021 while Annual Accounts revenue continues or grows --- diagnosed as installation-level reclassifications under Phase IV, not real abatement. NACE 21 shows no analogous pattern.
\end{itemize}

\subsection{Specification}
Decompose total emissions change as
\begin{equation}
  E_{t_1} - E_{t_0} \;=\; \underbrace{\text{Scale}_S + \text{Between}_S + \text{Within}_S + \text{Technique}_S}_{\text{survivor portion}} \;+\; \underbrace{E_{t_1, N}}_{\text{Entry}} \;-\; \underbrace{E_{t_0, X}}_{\text{Exit}},
\end{equation}
with the survivor portion computed by the standard Grossman--Krueger counterfactuals:
\begin{align*}
  \text{Scale}_S     &= Y_{t_1,S} \textstyle\sum_{i \in S} \theta_{i,t_0}^S z_{i,t_0} - E_{t_0,S}, \\
  \text{Between}_S   &= Y_{t_1,S} \textstyle\sum_{s} (\theta_{s,t_1}^S - \theta_{s,t_0}^S) z_{s,t_0}, \\
  \text{Within}_S    &= Y_{t_1,S} \textstyle\sum_{i \in S} \theta_{i,t_1}^S z_{i,t_0} - Y_{t_1,S} \sum_s \theta_{s,t_1}^S z_{s,t_0}, \\
  \text{Technique}_S &= Y_{t_1,S} \textstyle\sum_{i \in S} \theta_{i,t_1}^S (z_{i,t_1} - z_{i,t_0}).
\end{align*}
The six channels sum to $E_{t_1} - E_{t_0}$ exactly. Each is reported in pp of $E_{t_0}$.

\subsection{Results}

\begin{center}
\captionof{table}{Six-channel pairwise decomposition. pp columns sum to \textbf{Total}. $\bar z^E$, $\bar z^X$ in tCO\textsubscript{2} per million EUR.}
\footnotesize
\begin{tabular}{lrrrrrrrrrrrr}
\toprule
Pair & n\_s & n\_e & n\_x & Total & Scale & Btw & Within & Tech & Entry & Exit & $\bar z^E$ & $\bar z^X$ \\
\midrule
2005 $\to$ 2007 & 154 & 8  & 8  & $-4.1$  & $+18.2$ & $+11.5$ & $+3.3$  & $-38.1$ & $+1.0$  & $-0.1$ & 183 & 130 \\
2005 $\to$ 2012 & 127 & 37 & 35 & $-16.4$ & $+10.8$ & $+7.4$  & $+10.5$ & $\mathbf{-49.6}$ & $+10.8$ & $-6.4$ & 671 & 382 \\
2005 $\to$ 2020 & 105 & 55 & 57 & $-20.3$ & $+1.6$  & $-14.3$ & $+11.1$ & $-21.5$          & $+10.3$ & $-7.4$ & 466 & 298 \\
2005 $\to$ 2022 $^{\ddagger}$ & 99  & 49 & 61 & $\mathbf{-24.9}$ & $+15.9$ & $-35.1$ & $+4.9$  & $\mathbf{-11.6}$ & $+10.2$ & $-9.2$ & 369 & 286 \\
2007 $\to$ 2012 & 129 & 35 & 33 & $-12.8$ & $-6.6$  & $-3.9$  & $+4.0$  & $-10.4$          & $+10.8$ & $-6.7$ & 804 & 362 \\
2007 $\to$ 2020 & 109 & 51 & 53 & $-16.8$ & $-12.6$ & $-18.5$ & $+9.3$  & $\mathbf{+2.6}$  & $+9.5$  & $-7.1$ & 534 & 231 \\
2007 $\to$ 2022 $^{\ddagger}$ & 103 & 45 & 57 & $\mathbf{-21.1}$ & $+0.7$  & $-32.0$ & $+5.0$  & $\mathbf{+4.8}$  & $+9.4$  & $-9.0$ & 442 & 227 \\
2012 $\to$ 2020 & 126 & 34 & 38 & $-4.7$  & $-7.0$  & $-17.1$ & $+14.5$ & $\mathbf{+4.2}$  & $+3.1$  & $-2.3$ & 383 & 158 \\
2012 $\to$ 2022 $^{\ddagger}$ & 120 & 28 & 41 & $\mathbf{-12.6}$ & $+6.8$  & $-29.5$ & $+11.1$ & $\mathbf{-0.9}$  & $+2.9$  & $-2.9$ & 334 & 170 \\
\midrule
\multicolumn{13}{l}{\emph{Triple-balanced panel (101 firms present in 2005, 2012, and 2020):}}\\
2005 $\to$ 2012 $^{\dagger}$          & 101 & 0 & 0 & $-22.2$ & $+12.5$ & $+9.2$  & $+9.8$  & $\mathbf{-53.7}$ & 0     & 0       & --- & --- \\
2012 $\to$ 2020 $^{\dagger}$          & 101 & 0 & 0 & $-3.3$  & $-9.1$  & $-16.2$ & $+12.5$ & $\mathbf{+9.5}$  & 0     & 0       & --- & --- \\
2005 $\to$ 2020 $^{\dagger}$          & 101 & 0 & 0 & $-24.8$ & $+2.2$  & $-15.9$ & $+12.0$ & $-23.1$          & 0     & 0       & --- & --- \\
2020 $\to$ 2022 $^{\dagger\ddagger}$  &  96 & 0 & 3 & $-3.8$  & $+12.5$ & $-13.5$ & $-8.7$  & $\mathbf{+6.4}$  & 0     & $-0.4$  & --- & --- \\
\bottomrule
\end{tabular}
\captionof{table}{$^{\dagger}$Triple-balanced subset (firms with positive emissions in 2005, 2012, and 2020). $^{\ddagger}$Rows ending in 2022 exclude three contaminated firms from every year: one NACE 24 (likely ArcelorMittal Gent, 4.6 Mt $\to$ 0.09 Mt over 2020--2022 while revenue grew from 3{,}399 to 6{,}476 M\euro{}) and two NACE 20 firms whose EUTL verified emissions and free allocation collapse to near-zero in 2021 while revenue continues or grows. Diagnosed as installation-level reclassifications, not real abatement. The 2020 $\to$ 2022 row applies both markers: restricted to the triple-balanced firms and further excluding the three reclassifications (99 firms remain). The unrestricted 2005 $\to$ 2022 row would have been Total $-37.3$ with Technique $-25.6$; about $-12$ pp of Total and $-14$ pp of Technique there were artefact.}
\end{center}

\paragraph{Takeaway --- the full-horizon picture (2005 $\to$ 2022).} EU ETS emissions in Belgium fell $25\%$ between 2005 and 2022 on the clean panel. This is the net of two large channels pulling emissions down --- between-sector reallocation ($-35$ pp) and within-firm abatement ($-12$ pp) --- partially offset by real output growth of the surviving firms ($+16$ pp) and a small positive within-sector share shift toward dirtier firms ($+5$ pp). Entry and exit roughly cancel ($+1$ pp net).

\paragraph{Takeaway --- the two phases.} The fall is not uniform across time. Between 2005 and 2012 emissions fell $16\%$, and the within-firm abatement channel alone would have delivered a $50\%$ fall: technique $= -49.6$, while scale ($+10.8$), between-sector ($+7.4$), and within-sector ($+10.5$) were all pushing emissions up. Between 2012 and 2022 the picture inverts. Emissions fell only $13\%$, the technique channel essentially disappears (technique $= -0.9$), and between-sector reallocation carries almost the entire decline ($-29.5$). The conclusion is that the abatement story is almost entirely a Phase I/II phenomenon; from 2012 onward the emissions decline comes from the Belgian manufacturing mix shifting away from high-emission sectors, not from surviving ETS firms getting cleaner.

\paragraph{Takeaway --- the triple-balanced panel.} Restricting to the 101 firms present in 2005, 2012, and 2020 --- a strict same-firm comparison that rules out sample composition changes --- sharpens the phase contrast. On these 101 firms, technique is $\mathbf{-53.7}$ pp over 2005$\to$2012 (rapid Phase I/II abatement) but $\mathbf{+9.5}$ pp over 2012$\to$2020 (the earlier intensity reductions partially reversed). Extending to 2020$\to$2022 on the same panel, further excluding the three post-2020 reclassifications to leave 99 firms, technique is $\mathbf{+6.4}$ pp. So across 2012$\to$2022 on essentially the same firms, technique has been strictly positive: within-firm emission intensity among the long-survivors has been drifting \emph{up}, not down, for a decade.

\section{Sector-level heterogeneity}
\label{sec:sector}

\textbf{Script:} \texttt{analysis/phase0\_pairwise\_decomposition\_by\_sector.R}.

The aggregate pairwise decomposition in \S\ref{sec:pairwise} masks large differences across sectors. This section runs the same decomposition inside each NACE 2-digit sector separately, for the 2005$\to$2022 horizon. At single-sector level the \emph{Between-sector} channel collapses (only one sector), so the decomposition has five channels --- Scale, Within (firm-share shifts inside the sector), Technique, Entry, Exit --- that sum to the sector's own Total in pp of its own 2005 emissions. The three contaminated VATs (\S\ref{sec:pairwise}) are excluded from every year.

\subsection{Results}

\begin{center}
\captionof{table}{Per-sector decomposition, 2005 $\to$ 2022. All pp of the sector's own 2005 emissions; five channels sum to \textbf{Total}. ``\% of agg.'' is the sector's share of aggregate 2005 ETS emissions.}
\small
\begin{tabular}{llrrrrrrrrrr}
\toprule
NACE & Sector & \% of agg. & n\_s & n\_e & n\_x & Total & Scale & Within & Tech & Entry & Exit \\
\midrule
35 & Electricity               & 43.3 &  3 &  4 &  1 & $\mathbf{-39.8}$ & $-46.4$ & $+12.8$           & $-15.7$          & $+9.7$  & $-0.1$  \\
23 & Cement, glass, ceramics   & 21.3 & 21 & 11 &  7 & $\mathbf{-29.0}$ & $+11.3$ & $\mathbf{-15.1}$  & $\mathbf{-25.8}$ & $+4.9$  & $-4.2$  \\
19 & Petroleum refining        & 13.2 &  3 &  1 &  2 & $+1.6$           & $-32.1$ & $+16.0$           & $+28.8$          & $+0.2$  & $-11.3$ \\
20 & Chemicals                 &  9.3 & 26 & 21 &  5 & $\mathbf{+43.7}$ & $-29.7$ & $+24.4$           & $+14.2$          & $+42.2$ & $-7.5$  \\
24 & Basic metals              &  7.5 &  6 &  3 &  5 & $\mathbf{-70.6}$ & $-0.9$  & $-7.1$            & $-0.2$           & $+2.9$  & $-65.3$ \\
17 & Paper                     &  1.7 &  5 &  1 &  4 & $-3.4$           & $+35.4$ & $+15.1$           & $-38.2$          & $+3.5$  & $-19.2$ \\
13 & Textiles                  &  0.2 &  3 &  3 &  7 & $-43.8$          & $-9.2$  & $+0.5$            & $+11.8$          & $+27.1$ & $-73.9$ \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Technique by phase}

Splitting by phase makes the heterogeneity in within-firm abatement stark:

\begin{center}
\captionof{table}{Within-firm technique channel, by sector and phase. pp of each sector's own $t_0$ emissions.}
\begin{tabular}{llrr}
\toprule
NACE & Sector & Tech 2005 $\to$ 2012 & Tech 2012 $\to$ 2022 \\
\midrule
35 & Electricity               & $\mathbf{-99.9}$ & $\mathbf{+39.1}$ \\
23 & Cement, glass, ceramics   & $-29.7$          & $-9.0$           \\
19 & Petroleum refining        & $+32.3$          & $-55.1$          \\
20 & Chemicals                 & $+42.0$          & $-20.5$          \\
24 & Basic metals              & $-5.4$           & $+13.9$          \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Takeaways}

\textbf{Which sectors account for the aggregate decline?} Electricity (NACE 35) and basic metals (NACE 24) drive most of it. Cement/glass (NACE 23) contributes a moderate decline. Petroleum (19) is essentially flat. \textbf{Chemicals (NACE 20) went the other way: emissions grew by 44\%} of the sector's 2005 baseline over 2005$\to$2022, driven by $+42$ pp of Entry (21 new ETS-reporting chemical firms joining the panel) plus a +14 pp rise in within-firm intensity among survivors.

\textbf{Within-firm abatement is far from consistent across sectors.} The electricity sector had spectacular Phase I/II abatement ($-100$\% of its 2005 emissions from Technique alone), but the 2012$\to$2022 technique is $+39$ pp: surviving thermal plants appear to be running at lower capacity factor as non-ETS renewables take over the grid, which mechanically raises their emissions per unit of their own real revenue. Cement/glass (23) is the only big sector with sustained within-firm abatement across both phases. Petroleum (19) and chemicals (20) both have a Phase I/II intensity \emph{rise} reversed post-2012, a pattern that cancels on net. Basic metals (24) on the non-reclassified survivors shows essentially no Technique in either phase; the 71-pp sector decline is overwhelmingly Exit.

\textbf{Within-sector reallocation exists and goes in both directions.} Cement/glass is the textbook H1 story: $-15.1$ pp of within-sector reallocation over 2005$\to$2022 ($-16.3$ in 2012$\to$2022 alone). Dirtier firms lost share to cleaner ones inside that sector. The opposite happens in electricity ($+12.8$), petroleum ($+16.0$), and especially chemicals ($+24.4$): dirtier firms \emph{gained} share within the sector. The aggregate within-sector reallocation of $+4.9$ pp in \S\ref{sec:pairwise} is the weighted average: the dirty-gaining effect in the large chemicals, petroleum, and electricity sectors outweighs the clean-gaining effect in cement/glass.

\textbf{What this implies for the broader story.} The paper's main within-sector-reallocation null is not uniform. There is a clean reallocation story in NACE 23 --- exactly the sector where \cite{phase3}'s pass-through evidence is strongest --- and opposite-signed within-sector reallocation elsewhere. Any H1 vs H2 test that pools across sectors will wash out the cement signal. A sector-by-sector treatment (or at least a split that isolates NACE 23) is a natural follow-up.

\section{Sector-phase dataset: allocation rules and channel responses}
\label{sec:sectorphase}

\textbf{Script:} \texttt{analysis/phase0\_sector\_phase\_dataset.R}.

\subsection{Motivation and construction}

The sector decomposition in \S\ref{sec:sector} is silent on timing: it pools 2005--2022 (or phases it into two halves). This section slices the same five-channel decomposition by the four official EU ETS phases and merges it with the allocation rule in force in each sector-phase, so that we can ask whether the sector heterogeneity above tracks the sector-specific timing of allocation-rule changes.

Phase windows used for the within-phase decomposition:
\begin{center}
\begin{tabular}{llllll}
\toprule
Phase & Window & ``Paying'' starts & Känzig learning date & Event \\
\midrule
Phase 1 & $2005 \to 2007$ & 2005-01-01 & 2003-10-13 & Directive 2003/87/EC (pre-K\"anzig sample) \\
Phase 2 & $2008 \to 2012$ & 2008-01-01 & 2005-06-20 & First K\"anzig surprise \\
Phase 3 & $2013 \to 2020$ & 2013-01-01 & \textbf{2009-04-23} & Directive 2009/29/EC adopted (4-year anticipation) \\
Phase 4 & $2021 \to 2022$ & 2021-01-01 & \textbf{2018-03-14} & Directive 2018/410 adopted (3-year anticipation) \\
\bottomrule
\end{tabular}
\end{center}
Phase 3 ends 2020 to avoid the EUTL reclassifications that contaminate 2021+; Phase 4 is only 2 years of available data and the three contaminated VATs are excluded.

Allocation-rule coding at NACE 2d, based on Commission Decisions 2010/2/EU, 2014/746/EU, and 2019/708/EU:
\begin{itemize}
  \item \texttt{grandfathered\_free} --- Phase 1 and Phase 2 for all sectors (free allocation based on historical activity).
  \item \texttt{full\_auction} --- Phase 3 onwards for electricity (NACE 35).
  \item \texttt{CL\_list\_free} --- Phase 3/4 for sectors on the Carbon Leakage list (cement 23, petroleum 19, basic metals 24, chemicals 20, parts of paper 17). Free allocation indexed to a product benchmark $\times$ historical activity level.
  \item \texttt{partial\_free\_declining} --- Phase 3/4 for non-CL industrials (food 10, beverages 11, textiles 13, pharma 21, rubber/plastics 22). Free share declines from 80\% in 2013 toward 30\% in 2020, lower in Phase 4.
\end{itemize}
The NACE-2d granularity is approximate (see caveat below).

\subsection{Results --- Tech and Within by phase, top sectors}

\begin{center}
\captionof{table}{Within-firm technique and within-sector reallocation, by phase, for the five sectors that together account for $\sim 95\%$ of 2005 ETS emissions. pp of each sector's own phase-start emissions. Three contaminated VATs excluded from every year.}
\small
\begin{tabular}{lcrrrrrrrr}
\toprule
 & Phase 3/4 rule & \multicolumn{4}{c}{Technique} & \multicolumn{4}{c}{Within-sector reallocation} \\
\cmidrule(lr){3-6} \cmidrule(lr){7-10}
Sector & & P1 & P2 & P3 & P4 & P1 & P2 & P3 & P4 \\
\midrule
35 Electricity            & \texttt{full\_auction}            & $\mathbf{-74.6}$ & $-18.0$ & $\mathbf{+19.1}$ & $\mathbf{+20.4}$ & $+14.5$ & $+3.3$  & $-6.2$           & $-3.1$ \\
23 Cement, glass          & \texttt{CL\_list\_free}           & $-5.8$           & $-14.4$ & $\mathbf{-27.3}$ & $+10.8$           & $-4.0$  & $+5.8$  & $+13.4$          & $\mathbf{-15.1}$ \\
19 Petroleum refining     & \texttt{CL\_list\_free}           & $+5.2$           & $+8.9$  & $\mathbf{-42.4}$ & $-11.3$           & $-23.3$ & $-4.9$  & $\mathbf{+83.1}$ & $+2.2$ \\
20 Chemicals              & \texttt{CL\_list\_free}           & $-5.1$           & $+25.0$ & $-11.1$          & $\mathbf{-23.6}$  & $+3.3$  & $+7.5$  & $+13.5$          & $+2.9$ \\
24 Basic metals           & \texttt{CL\_list\_free}           & $+27.7$          & $-9.4$  & $\mathbf{-25.9}$ & $-6.2$            & $-51.6$ & $-1.2$  & $+13.3$          & $+2.0$ \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Three patterns}

\textbf{(1) For electricity, auctioning did not deliver more within-firm abatement --- the opposite.} The largest technique decline came in Phase 1 under grandfathered free allowances ($-75$ pp). When full auctioning kicked in at the start of Phase 3, technique \emph{reversed} to $+19$, and again $+20$ in Phase 4. Scale over the same Phase 3 window was $-27$: the surviving thermal plants are running at much lower capacity factor as non-ETS renewables take over supply, which mechanically raises their emissions per unit of their own real revenue. Moving from free allowances to auctioning does not appear to have induced additional abatement in this sector; the headline emissions decline in Phase 3/4 is the output-contraction channel, not the intensity channel.

\textbf{(2) Carbon-leakage-list industrials delivered their biggest within-firm abatement in Phase 3.} Cement ($-27$), petroleum ($-42$), basic metals ($-26$), and chemicals ($-11$ then $-24$ in Phase 4) all show a Phase 3 technique that is more negative than anything these sectors produced in the grandfathered phases. These sectors' Phase 3/4 allocation rule pays firms for abating below the product benchmark (allowances indexed to activity at a benchmark intensity); a benchmark-based system creates a direct marginal incentive that pure grandfathering lacks. Chemicals' Phase 4 technique of $-24$ is consistent with the tightening of benchmarks under the Phase 4 linear reduction factor continuing to bite.

\textbf{(3) Within-sector reallocation is almost entirely a Phase 3/4 phenomenon.} Phases 1--2 show small magnitudes (mostly $|$Within$|\leq 5$ pp). In Phases 3--4, petroleum has a striking $+83$ (dirty firms gained share among survivors), chemicals $+14$, and basic metals $+13$. Cement is the clean-reallocation exception: $+13$ in Phase 3 but $\mathbf{-15}$ in Phase 4, dirty firms losing share only after the benchmark tightening arrives. Cement is consistently the sector whose behaviour most resembles what a ``carbon pricing causes reallocation'' model predicts.

\subsection{Anticipation vs.\ paying}

Phase 3 was adopted in April 2009 but firms only started paying for allowances (via auctioning for electricity, tighter benchmarks for industry) in January 2013. The $\sim 4$-year gap between \emph{learning} and \emph{paying} is directly observable in the K\"anzig surprise series: the 2009-04-23 surprise of $-0.12$ euros is Directive 2009/29/EC's adoption. Phase 2 (2008--2012) therefore covers exactly the Phase 3 anticipation window. Electricity's Phase 2 technique of $-18$ is one plausible reading of an anticipation response, but it is one-quarter the size of Phase 1's abatement and sits in the 2008--09 crisis window, so causal attribution is ambiguous. A focused decomposition over $2009 \to 2012$ (post-adoption, pre-payment) is a natural follow-up.

Phase 4 has the same structure with a shorter anticipation window: Directive 2018/410 adopted in March 2018, paying starts January 2021. K\"anzig's event series has large surprises concentrated around the Phase 4 trilogue and Council dates in 2018. Two years of post-2021 data is too little to identify a Phase 4 response cleanly; this is a ``come back in 2027'' question.

\subsection{Caveat on allocation-rule coding}

The Commission's Carbon Leakage list is defined at NACE 4-digit, not at NACE 2d. Coding each NACE 2d sector with a single allocation rule is an approximation that is inaccurate for several sectors --- most visibly chemicals (NACE 20), where plastics precursors and inorganic chemicals are on the CL list while downstream formulation activities are not. The patterns above are robust to this concern only when the sector-level headline is dominated by one sub-sector (electricity 35, basic metals 24 are clean; chemicals 20 is the main worry).

Refining this for the \emph{descriptive} decomposition buys little. We already observe $\mathrm{shortage}_{i,t} = \max(\mathrm{emissions} - \mathrm{free\_allocation},\, 0)$ directly at firm-year, so the question ``who pays how much'' is already identified without a 4d crosswalk. The 4d CL list is valuable for \emph{identification}, specifically the anticipation channel: a firm in a 4d sector that stays on the CL list after (e.g.) the 2014-05 revision learns it will keep free allocation, while one removed from the list learns it will face declining free allocation starting in 2015+. That asymmetric announcement is a clean cross-sectional test of whether firms invest in abatement in response to \emph{news} about future carbon costs, not to realized costs --- but that's a separate exercise with a different LHS (capex, energy intensity), and is tracked as the Threat-hypothesis Strategy C in \texttt{TODO.md} and \texttt{TREAT\_HYPOTHESIS\_PLAN.md}. For the descriptive exercise here, the 2d coarseness caveat stands, and the CL-list panel at 4d is deliberately deferred to that workstream.

\subsection{Three takeaways from the sector story}

\paragraph{Takeaway 1 --- electricity is hard to interpret using EU ETS firm-year data alone.} The $-75 \to +19 \to +20$ technique path for NACE 35 across phases does not reflect what firms are doing to their installations; it reflects that the same installations run fewer hours as non-ETS renewables crowd them out of the merit order. At firm-year granularity we cannot separate ``firm $X$ installed abatement technology'' from ``firm $X$ ran its plant at 40\% capacity instead of 80\%'', and for electricity the second channel is doing most of the work post-2012. Any emissions-per-real-revenue number for this sector is a capacity-factor measurement as much as a technology measurement.

\paragraph{Takeaway 2 --- substantial heterogeneity across sectors and across time.} The Phase 3 technique channel ranges from $-42$ (petroleum) to $+19$ (electricity), a 60-pp spread. Cement alone moves from $-6 \to -14 \to -27 \to +11$ across phases. Within-sector reallocation has even wider variation ($-15$ to $+83$ across sector-phase cells). There is no single ``ETS response'' pattern that applies economy-wide; each large sector has its own phase-specific story.

\paragraph{Takeaway 3 --- no clean paying-time connection outside electricity.} The framing of ``when does the firm start paying'' applies cleanly only to electricity because that is the only sector whose allocation rule has a discrete Phase 2 $\to$ Phase 3 switch (grandfathered $\to$ full auction). For CL-list industrials the allocation rule moves from grandfathered to benchmark $\times$ activity, but both regimes produce near-100\% free allowances in practice --- the firms never really start paying in the same sense; they just face a different marginal incentive. For non-CL industrials the free share declines gradually (80\% in 2013 to 30\% by 2020), so there is no single moment either. The CL-list industrials do show their largest within-firm technique declines in Phase 3 (cement $-27$, petroleum $-42$, metals $-26$), consistent with the Phase 3 benchmark system rewarding intensity improvements more directly than grandfathering did. But we cannot separate that from general Phase 3 EU ETS cap tightening, EUA price movements, or autonomous technology trends without a cleaner identification strategy.

\section{ETS vs.\ non-ETS revenue reallocation}
\label{sec:etsvsnonets}

\textbf{Script:} \texttt{analysis/phase0\_ets\_vs\_nonets\_reallocation.R}.

Tests whether ETS firms' real revenue contracts relative to non-ETS firms within the same NACE 4d sector-year as the sector-specific carbon-cost shock rises. Replaces a predecessor exercise (which regressed sector-level ETS revenue shares on contemporaneous carbon-cost shares at NACE 2d) after six fixes documented below.

\subsection{Variables}
\begin{itemize}
  \item $\mathrm{ETS}_i \in \{0,1\}$: firm-level ETS-regulated status (from \texttt{firm\_year\_belgian\_euets}).
  \item $\mathrm{real\_rev}_{i,t}$: nominal turnover deflated by NACE 4d PPI (2d fallback).
  \item $\mathrm{intensity\_base}_s$: pre-MSR (2013--16 mean) carbon cost share of the ETS firms in NACE 4d sector $s$. Both numerator and denominator are pre-determined (sector total carbon cost / total cost, averaged over 2013--16). Source: \texttt{data/processed/phase3\_sector\_exposure.RData}.
  \item $\mathrm{EUA}_t$: annual mean EUA secondary-market price, 2005--2022.
  \item $\mathrm{shock}_{s,t} = 100 \cdot \mathrm{intensity\_base}_s \times \mathrm{EUA}_t$: Bartik-style shock, pre-determined sector exposure interacted with the aggregate EUA path. Only the aggregate EUA scalar moves; the Belgian ETS firms cannot collectively move it.
  \item \textbf{Non-ETS firm universe:} union of \texttt{training\_sample} (non-ETS component; firms in NACE 17, 18, 19, and the zero-24 sub-sectors, for which emissions are imputed to zero in the preprocessing pipeline) and \texttt{deployment\_panel} (non-ETS firms in all other sectors), deduplicated. The zero-sector non-ETS firms live only in \texttt{training\_sample} and were omitted from the predecessor regression; recovering them adds 2,959 non-ETS firms including all the non-ETS competitors in the paper and petroleum sectors.
  \item \textbf{Mixed-sector restriction:} only the 92 NACE 4d sectors with at least one ETS and at least one non-ETS firm present in $\geq 1$ year.
  \item \textbf{Contamination filter:} three ETS VATs that come off EUTL reporting in 2021 (\S\ref{sec:pairwise}) excluded from every year.
\end{itemize}

\subsection{Specification}

\textbf{Main spec (log levels, firm + sector-year FE):}
\begin{equation}
  \log(\mathrm{real\_rev})_{i,s,t} = \beta \cdot (\mathrm{ETS}_i \times \mathrm{shock}_{s,t}) + \gamma \cdot (\mathrm{ETS}_i \times \mathrm{EUA}_t) + \alpha_i + \alpha_{s,t} + \varepsilon_{i,s,t}.
\end{equation}
\begin{itemize}
  \item $\alpha_i$ (firm FE) absorbs ETS status, firm-invariant sector, time-invariant scale.
  \item $\alpha_{s,t}$ (NACE 4d $\times$ year FE) absorbs \emph{all} sector-year macro variation, including the main effect of $\mathrm{shock}_{s,t}$ itself.
  \item $\beta$: within a 4d sector-year, how much more does an ETS firm's log real revenue move with $\mathrm{shock}_{s,t}$ than a non-ETS firm's in the same sector-year. Under H1 (reallocation), $\beta < 0$.
  \item $\gamma$: common ETS-vs-non-ETS time trend with EUA, independent of sector exposure. Not of primary interest but kept in to avoid confounding.
  \item SEs clustered on NACE 4d.
\end{itemize}

\subsection{Identification assumption}

Three layers of FE absorption:
\begin{itemize}
  \item Firm FE removes ETS status, time-invariant sector, scale. The dominant confounder --- that ETS firms are systematically much larger (mean log-real-revenue gap $\approx 3.45$, i.e.\ $\sim 31 \times$ larger) --- is absorbed here.
  \item 4d $\times$ year FE removes all sector-year macro, including the main effect of $\mathrm{shock}_{s,t}$ and of $\mathrm{EUA}_t$ itself.
  \item Identification: residual variation in $\mathrm{ETS}_i \times \mathrm{shock}_{s,t}$ within a 4d sector-year cell (binary across firms, scaled by $\mathrm{shock}_{s,t}$), compared across cells where $\mathrm{shock}_{s,t}$ varies through its $\mathrm{EUA}_t$ component.
\end{itemize}

Assumption: conditional on firm and 4d $\times$ year FE, $\mathrm{shock}_{s,t}$ is uncorrelated with other determinants of the ETS-vs-non-ETS revenue gap. Fails if macroeconomic shocks that raise EUA differentially affect ETS vs non-ETS firms in ways unrelated to carbon cost (e.g., ETS firms tend to be exporters, and EUA co-moves with the exchange rate). The Bartik structure (sector-fixed intensity $\times$ aggregate EUA) mitigates but does not eliminate this.

\subsection{Results}

\begin{center}
\captionof{table}{ETS $\times$ shock coefficients. Standard errors clustered on NACE 4d. Sample: 80{,}932 firm-years in 92 mixed NACE 4d sectors, 2005--2022.}
\begin{tabular}{lrrrr}
\toprule
Specification & $\hat\beta$ & SE & $t$ & $p$ \\
\midrule
Main: firm FE + 4d $\times$ year FE                   & $-0.026$ & $0.017$ & $-1.50$ & $0.14$ \\
Robustness: 4d + year FE (no firm FE)                 & $-0.168$ & $0.059$ & $-2.83$ & $0.006$ \\
Robustness: first differences, firm FE + 4d $\times$ year FE & $+0.019$ & $0.022$ & $+0.89$ & $0.38$ \\
Simpler: $\mathrm{ETS}_i \times \mathrm{EUA}_t$ only (no sector interaction) & $-0.0009$ & $0.001$ & $-0.75$ & $0.46$ \\
\bottomrule
\end{tabular}
\end{center}

\textbf{Main result: direction consistent with reallocation, not significant.} With firm and sector-year FE, $\hat\beta = -0.026$ ($p = 0.14$): within a 4d sector-year, ETS firms' log real revenue falls by 0.026 for every 1-unit rise in $\mathrm{shock}$ compared to non-ETS firms in the same sector-year. Negative, consistent with H1, but below conventional significance.

\textbf{The no-firm-FE spec gives a large significant negative, but it is contaminated.} The 4d + year FE spec delivers $\hat\beta = -0.168$ ($p = 0.006$). That estimate is not credible because without firm FE, ETS firms' systematic size advantage ($\exp(3.45) \approx 31\times$ larger in mean real revenue) correlates with sector dirtiness and inflates the estimated reallocation slope.

\textbf{First differences is null.} Taking $\Delta \log(\mathrm{real\_rev})$ on $\Delta \mathrm{shock}$ with firm FE yields $\hat\beta = +0.019$ ($p = 0.38$). Consistent with the main spec in ruling out large short-run responses, at the cost of discarding the level information.

\textbf{Economic magnitude from the main spec.} At the main coefficient, with $\mathrm{shock}$ ranging up to $\sim 42$ in the dirtiest 4d sectors at peak EUA ($\mathrm{intensity\_base} \approx 0.005$, $\mathrm{EUA} = 80$ EUR in 2022), the implied log revenue differential for an ETS firm vs non-ETS in that cell is $-1.1$ ($\sim -66\%$ in levels). For the typical sector (median $\mathrm{intensity\_base} \approx 5 \times 10^{-6}$) the effect is effectively zero. The identified variation is concentrated in a handful of sectors (cement/glass 23, basic metals 24, petroleum 19, parts of chemicals 20) --- consistent with the sector-level heterogeneity in \S\ref{sec:sector}.

\textbf{Caveat: underpowered.} Across 92 mixed 4d sectors, only 15--20 have meaningful $\mathrm{intensity\_base}$. Power to detect reallocation is concentrated in those cells where both $\mathrm{intensity\_base}$ is non-trivial \emph{and} the sector has a mix of ETS and non-ETS firms. The null is compatible both with ``no reallocation effect'' and with ``real reallocation effect that we cannot detect with this sample''. A larger identification window (joint EU-wide data, or EUA extensions into 2023--24 pending new NBB data vintages) would help.

\section{Within-sector output shares by exposure tercile}

\textbf{Script:} \texttt{analysis/phase1a\_output\_share\_by\_exposure.R}. Eyeball/descriptive test.

\subsection{Variables}
\begin{itemize}
  \item $\mathrm{shortage\_intensity}_i$: firm-level pre-MSR shortage intensity, $\mathrm{mean}_{t \in 2013..16}[\mathrm{shortage}_{i,t} / q_{i,t}]$.
  \item Classify firms into terciles of $\mathrm{shortage\_intensity}_i$ within each NACE 4-digit sector.
  \item Track each tercile's average within-sector output share over time, normalized to 1 in the base year.
\end{itemize}

\subsection{Specification}
Descriptive: plot mean of $\theta_{i,s,t} / \theta_{i,s,2005}$ averaged within each tercile, over $t \in 2005..2023$. Four variants: binary split within NACE 2d, binary within NACE 4d, terciles across economy, terciles within NACE 4d.

\subsection{Identification assumption}
None; purely descriptive. The interpretation as evidence for/against within-sector reallocation by exposure rests on (a) the tercile being a good pre-MSR exposure proxy, (b) there being no confounding within-sector variation that correlates with exposure.

\subsection{Results}
Terciles within NACE 4d (the sharpest variant): a long-run gradual convergence pattern in which high-exposure firms have been slowly losing within-sector share since 2005. \textbf{No post-2017 break} --- if anything, the divergence slowed down after the MSR reform. Same pattern in the binary 4d split. The long-run trend predates carbon pricing becoming binding.

\section{Phase 4 Spec 1.A --- Firm-level panel LP of $\Delta\log(\text{real rev})$}
\label{sec:phase4}

\textbf{Script:} \texttt{analysis/phase4\_firm\_output\_reallocation.R}. The sharpest within-sector test so far. Currently only ID-A (annual Känzig CPShock) is implemented; ID-B (EUA level) and ID-C (event study) are on the TODO.

\subsection{Variables}
\begin{itemize}
  \item $\mathrm{firm\_cost\_share}_i = \dfrac{\mathrm{mean}_{t \in 2013..16}[\mathrm{shortage}_{i,t} \cdot \mathrm{EUA}_t]}{\mathrm{mean}_{t \in 2010..12}[\mathrm{mat\_inputs}_{i,t} + \mathrm{wage\_bill}_{i,t}]}$. Firm-level analog of sector $\mathrm{intensity\_base}_s$: numerator averaged 2013--16, denominator averaged 2010--12 (fixed, pre-ETS-tightening). Fallback to earliest 3-year window for firms without 2010--12 coverage. Revenue is deliberately \emph{not} the denominator because revenue is endogenous to the ETS shock itself.
  \item $\mathrm{firm\_emint\_physical}_i = \dfrac{\mathrm{mean}_{t \in 2013..16} \mathrm{shortage}_{i,t}}{\mathrm{mean}_{t \in 2010..12} \mathrm{total\_cost}_{i,t}}$: robustness variant without EUA price in the treatment. Units tCO\textsubscript{2}/\euro.
  \item $\mathrm{firm\_dev}_{i,s} = \mathrm{firm\_cost\_share}_i - \overline{\mathrm{firm\_cost\_share}}_s$: within-NACE-4d-sector demeaning. SD across firms $= 0.037$.
  \item $\mathrm{Signal}_t \in \{\mathrm{CPShock}^{\mathrm{surprise},\mathrm{ann}}_t, \mathrm{CPShock}^{\mathrm{shock},\mathrm{ann}}_t\}$: annual sum of Känzig (2025) monthly series. SDs $0.53$ and $2.4$ respectively.
  \item LHS: $\Delta \log(\mathrm{real\_rev})_{i,t,h} = \log(\mathrm{real\_rev})_{i,t+h} - \log(\mathrm{real\_rev})_{i,t-1}$, LP-style, $h \in \{0,1,2,3\}$.
\end{itemize}

\textbf{Treatment-build verification.} Aggregating $\mathrm{firm\_cost\_share}_i$ to NACE 4d with firm total-cost weights reproduces sector $\mathrm{intensity\_base}_s$ with correlation $0.98$ across 79 sectors (max abs.\ difference $0.003$). Passes.

\subsection{Specification}
\begin{equation}
  \Delta \log(\mathrm{real\_rev})_{i,s,t,h} = \beta \cdot (\mathrm{Signal}_t \times \mathrm{firm\_dev}_{i,s}) + \alpha_{s,t} + \alpha_i + \varepsilon_{i,s,t,h}. \label{eq:spec1A}
\end{equation}
$\alpha_{s,t}$ is a NACE 4d $\times$ year fixed effect; $\alpha_i$ a firm fixed effect. Two-way clustering on firm and sector-year. Sample: 215 firms, 2,163 firm-years at $h=0$, horizon window 2005--2019.

\subsection{Identification assumption}

Two assumptions:
\begin{enumerate}
  \item \textbf{Exogeneity of $\mathrm{Signal}_t$ to firm-level Belgian demand shocks conditional on $\alpha_{s,t}$.} For $\mathrm{CPShock}^{\mathrm{surprise}}$ this is the Känzig (2025) high-frequency event-study identification: surprise is measured in narrow windows around discrete EU ETS regulatory announcements, so it should be orthogonal to Belgian-specific demand conditions in year $t$. For $\mathrm{CPShock}^{\mathrm{shock}}$ the series is the VAR-instrumented response of the EUA price: it inherits VAR-level persistence and is not a clean high-frequency instrument. This is why we report both.
  \item \textbf{Exogeneity of $\mathrm{firm\_dev}_{i,s}$ to post-2016 firm-specific shocks.} $\mathrm{firm\_cost\_share}_i$ is built from 2010--16 firm data, so it pre-dates any 2017+ ETS tightening by construction. Survivorship bias through the 2010--12 and 2013--16 base-period filters is not addressed.
\end{enumerate}
Pre-trend placebo ($h = -2$) has not been run.

\subsection{Results}

\begin{center}
\captionof{table}{$\beta$ on $\mathrm{Signal}_t \times \mathrm{firm\_dev}_{i,s}$ (two-way cluster SEs).}
\begin{tabular}{lcc}
\toprule
Horizon & $\mathrm{cpshock\_surprise}$ & $\mathrm{cpshock\_shock}$ \\
\midrule
$h=0$ & $-5.66\ (0.90),\ p<0.001$ & $+0.58\ (0.22),\ p=0.008$ \\
$h=1$ & $-1.81\ (2.72),\ p=0.51$  & $+1.08\ (0.33),\ p=0.001$ \\
$h=2$ & $-2.32\ (3.46),\ p=0.50$  & $+1.66\ (0.40),\ p<0.001$ \\
$h=3$ & $-2.65\ (3.32),\ p=0.42$  & $+1.60\ (0.37),\ p<0.001$ \\
\bottomrule
\end{tabular}
\end{center}

Signs flip between the two signal variants at every horizon. Magnitudes on $\mathrm{surprise}$ are implausibly large; magnitudes on $\mathrm{shock}$ are quantitatively reasonable but wrong-signed under H1 (high-exposure firms \emph{gain} output when the carbon price rises). Same pathology as \cite{passthrough}'s S7--S11 specifications. Robustness with $\mathrm{firm\_emint\_physical}_i$ preserves signs and significance at every horizon. \emph{Under ID-A, no direction can be read from this exercise until the surprise-vs-shock sign flip is diagnosed.}

\section{Phase 4 Spec 1.C --- Sample split by realized sector pass-through}

\textbf{Scripts:} \texttt{analysis/phase4\_sector\_passthrough\_classification.R} and \texttt{analysis/phase4\_firm\_output\_reallocation.R}. Addresses H1 (within-sector reallocation) vs H2 (inelastic-demand shield) by checking whether firm-level reallocation is concentrated in sectors that actually pass costs through.

\subsection{Variables}
\begin{itemize}
  \item $\gamma_s$: sector-specific monthly PPI response to CPShock at $h=12$ months, estimated from an interacted panel LP (see specification below).
  \item Classification of each sector into \emph{high-pass-through}, \emph{no-pass-through}, or \emph{unclassified} using $\gamma_s$ and its SE. Six cutoffs: sign under shock, sign under surprise, top tercile, $t>1.645$, $t>1.96$, and intersection of sign under both shock and surprise variants.
  \item All variables from \S\ref{sec:phase4}.
\end{itemize}

\subsection{Specification}

\textbf{Step 1 (sector classification):}
\begin{equation*}
  \Delta \log(\mathrm{PPI})_{s,m+12} - \Delta \log(\mathrm{PPI})_{s,m-1}
  = \sum_s \gamma_s \cdot \mathrm{CPShock}_m \cdot \mathbf{1}(\mathrm{sector}=s)
    + \alpha_s + \delta_m + \varepsilon_{s,m},
\end{equation*}
estimated on the monthly 2005--2019 panel (same as the S12 headline). Clustered on year-month (clustering on NACE 4d would be degenerate since each $\gamma_s$ lives in a single cluster). 133 sectors obtain a coefficient.

\textbf{Step 2 (sample-split Spec 1.A):} re-estimate equation~\eqref{eq:spec1A} on each subsample.

\subsection{Identification assumption}

Inherits \S\ref{sec:phase4}'s two assumptions. Adds:
\begin{itemize}
  \item $\gamma_s$ must be a reasonable proxy for the sector's realized pass-through elasticity. The main concern is noise: with $\sim 180$ months per sector and $|\mathrm{CPShock}|$ modest, $\gamma_s$ is imprecisely estimated, so the \emph{no-pass-through} bucket will contain both true non-passers and sectors that pass through but couldn't be distinguished statistically. Classification is therefore conservative toward H1 (false negatives likely, false positives less likely).
\end{itemize}

\subsection{Results --- selected cells}

Split by $\mathrm{cpshock\_shock}$ sign (41 high-pass-through sectors, 122 firms; 7 no-pass-through sectors, 10 firms):

\begin{center}
\begin{tabular}{lcccc}
\toprule
Horizon & High / surprise & High / shock & No / surprise & No / shock \\
\midrule
$h=0$ & $-9.49$        & $+1.63$       & $+2.12$  & $-31.8$ \\
$h=1$ & $-12.83$       & $+1.02$       & $+225.5$ & $-65.0$ \\
$h=2$ & $\mathbf{-37.67^{**}}$ & $\mathbf{+4.14^{***}}$ & $+162.6$ & $\mathbf{-132.0^{***}}$ \\
$h=3$ & $\mathbf{-35.85^{**}}$ & $\mathbf{+2.91^{*}}$   & $+150.0$ & $\mathbf{-124.8^{***}}$ \\
\bottomrule
\end{tabular}
\captionof{table}{$\beta$ in sample-split Spec 1.A. Bold = significant at 5\% (or 10\% for single-star).}
\end{center}

Similar patterns under top-tercile and 10\%-significance cutoffs: the H1-direction coefficient ($\mathrm{surprise}$, negative at $h \geq 2$) is driven by the \emph{high-pass-through} subsample, consistent with H1 over H2. But the sign flip across shock-vs-surprise survives in every cut, and the ``no-pass-through'' subsample's coefficients are wild (often $\pm 100+$) because the cell is too small.

\subsection{Caveats}
\begin{itemize}
  \item The $\mathrm{shock}$-based classification is nearly non-discriminating (118 of 133 sectors have $\gamma_s > 0$); the $\mathrm{surprise}$ classification is too noisy at NACE 4d (no sector reaches $t > 1.645$). A rank-based classification is on the TODO (follow-up B).
  \item Magnitudes under $\mathrm{Signal}=\mathrm{cpshock\_surprise}$ are implausible at face value: $\beta \approx -37$ with $\mathrm{SD}(\mathrm{firm\_dev}) = 0.037$ and $\mathrm{SD}(\mathrm{surprise}) = 0.53$ implies a $-72\%$ cumulative log real-revenue response to a 1-SD$\times$1-SD interaction, which the data cannot literally support.
  \item Until the shock-vs-surprise sign flip is diagnosed (follow-up A), sign interpretation under ID-A is not trustworthy.
\end{itemize}

\section{Summary of reallocation tests}

\begin{center}
\begin{tabular}{p{5.5cm}p{4cm}p{5cm}}
\toprule
Test & Level & Finding \\
\midrule
Pairwise decomposition                    & Aggregate, ETS firms                      & Post-2012 decline is all Between-sector; aggregate Within-sector $\approx +5$ pp \\
Sector-level heterogeneity                & NACE 2d, ETS firms                        & Cement (23) shows clean reallocation ($-15$); electricity/petroleum/chemicals show dirty gaining; aggregate null masks the split \\
ETS vs.\ non-ETS revenue reallocation     & NACE 4d, firm panel, firm + 4d$\times$year FE & $\hat\beta = -0.026$ (p$=0.14$) on ETS $\times$ Bartik shock; direction consistent with H1 but underpowered \\
Binary split by exposure, NACE 4d         & Within NACE 4d, ETS firms                 & Flat post-2017 \\
Terciles within sector                    & Within NACE 4d, ETS firms                 & Long-run trend, no post-2017 break \\
Phase 4 Spec 1.A (pooled)                 & Firm-year panel LP under ID-A             & Sign flip across shock/surprise; uninterpretable \\
Phase 4 Spec 1.C (sample split)           & Firm-year panel LP, high-pass-through sectors & Negative under surprise $h\geq 2$, positive under shock; same flip \\
\bottomrule
\end{tabular}
\end{center}

\textbf{Bottom line.} Across every pre-Phase-4 test, within-sector reallocation is approximately zero or uncorrelated with carbon cost exposure. Phase 4 Spec 1.A/1.C under ID-A cannot deliver a directional answer until the shock-vs-surprise sign flip is understood. Identifications ID-B (EUA level) and ID-C (event study), plus Angle 4 (B2B supplier switching), remain to be run.

\begin{thebibliography}{99}
\bibitem[K\"anzig(2025)]{kanzig2025} K\"anzig, D.~R. (2025). ``The Unequal Economic Consequences of Carbon Pricing.''
\bibitem[Phase 3 notes]{phase3} Internal: \texttt{phase3\_build\_exposure\_panel.R}.
\bibitem[Pass-through notes]{passthrough} Internal: \texttt{PASSTHROUGH\_CPSHOCK.md}, S7--S12.
\end{thebibliography}

\end{document}
