We estimate the elasticity of substitution between carbon-regulated and unregulated suppliers in Belgian firm-to-firm transactions, using the post-2017 EU ETS price increment as the cost shock to regulated suppliers. Our preferred bound on the within-NACE-4d, across-supplier margin places $\sigma \in [0.74, 1.26]$ at the 95\% confidence level under our preferred conservative pass-through assumption $\rho = 0.5$, with point estimate at $\sigma = 1.0$. Under full pass-through $\rho = 1$, the bound tightens to $\sigma \in [0.87, 1.13]$, and the larger sample to $\sigma \in [0.85, 1.03]$. The across-category margin gives a wider but consistent bound, $\sigma_{\text{cat}} \in [0.5, 5.0]$ centered at $1.05$. Both margins place $\sigma$ tightly around the Cobb-Douglas benchmark and rule out, at conventional confidence levels, the elasticities typically estimated in import-substitution work for differentiated intermediates.

The reduced-form coefficients underlying these bounds are precisely zero: on the within-NACE-4d margin, the headline pair-exposure regression returns a pooled $\beta = -16.7$ (s.e.\ $17.4$), the linear-trend-controlled specification $+5.4$ (s.e.\ $20.4$, with the trend coefficient itself not statistically distinguishable from zero), and the most-favorable Q4 subset $\beta = +0.03$ (s.e.\ $1.39$); on the across-category margin, the binary regulated $\times$ \textit{Post} specification yields $\beta = -0.003$ (s.e.\ $0.009$, $p = 0.76$). In the CES mapping, precisely-zero $\beta$'s map directly to a precise Cobb-Douglas point estimate. A standard Grossman--Krueger emissions decomposition on the same window confirms the same pattern from the supplier side: within-sector reallocation accounts for essentially zero of the 46\% aggregate emissions decline.

The data are consistent with several non-mutually-exclusive mechanisms for an elasticity centered near unity. The most natural first guess --- that shock magnitudes at the typical pair are too small to detect substitution --- has the \emph{least} direct empirical support: at the right tail of pair-exposure, where the shock is large enough to identify $\sigma \approx 4$ in \citet{peter2023}'s setting, the coefficient is wrong-signed for substitution and not statistically distinguishable from the pooled estimate, cutting against a heterogeneous-$\sigma$-by-shock-size story. The remaining mechanisms have stronger empirical purchase: relational capital in Belgian B2B (pairs older than five years carry $\sim$79\% of total trade); the prevalence of regulated alternatives within the same NACE 4-digit in heavy-emitting sectors; partial supplier-side pass-through; and buyer-side pass-through onto downstream customers. We cannot separately identify these mechanisms with the current data. A small but statistically detectable extensive-margin response qualifies the intensive-margin estimate but does not overturn the implied $\sigma$.

We do not interpret our $\sigma$ estimate as time-invariant or as a prediction about reallocation at higher carbon prices. Whether reallocation would appear at $\sim$2.5$\times$ the realized 2022 EUA price --- where right-tail pair-shock magnitudes would scale to match \citet{peter2023}'s p95 imported-input shock --- is a question we cannot answer with current data, and we leave it open. Within the policy-relevant Phase~III/IV window, our estimate provides a direct micro-foundation for the substitution parameter that disciplines quantitative production-network models of carbon policy: it points to Cobb-Douglas, not toward the larger import-substitution elasticities, and the implications for aggregate carbon-pricing counterfactuals are consequential.
