This section bounds what the joint null can and cannot say. The headline of the paper is that, on observable substitution at two reallocation margins, we find no statistical evidence of buyer-side reallocation in response to the EU ETS in Belgium. This is an observational null, not a structural identification of the elasticity of substitution. We discuss four issues: bounds on the elasticity of substitution, candidate explanations for why the elasticity is consistent with our null, selection, and external validity.

\subsection{Bounds on the elasticity of substitution}\label{sec:bounds}

The regression coefficients in Sections~\ref{sec:test_h} and~\ref{sec:test_i} can be mapped, under standard assumptions, to bounds on the elasticity of substitution $\sigma$. We make the assumptions explicit and report the bounds as suggestive rather than structural.

\paragraph{Mapping coefficients to $\sigma$.} Consider a CES nest where buyer $b$ allocates expenditure across suppliers $j$ in NACE 4-digit category $n$, with elasticity $\sigma$ across suppliers. For small price changes,
\[
    \mathrm{d}\log s_{j} \;=\; (1 - \sigma)\,\bigl(\mathrm{d}\log p_{j} \;-\; \mathrm{d}\log P_n\bigr),
    \qquad
    \mathrm{d}\log P_n \;=\; \sum_{k} s_k\,\mathrm{d}\log p_k.
\]
If only supplier $j^*$'s price changes, $\mathrm{d}\log p_{j^*} - \mathrm{d}\log P_n = (1 - s_{j^*})\,\mathrm{d}\log p_{j^*}$, and
\[
    \mathrm{d} s_{j^*} \;\approx\; s_{j^*}\,(1 - \sigma)\,(1 - s_{j^*})\,\mathrm{d}\log p_{j^*}.
\]
Under full pass-through, $\mathrm{d}\log p_{j^*} \approx \text{firm cost share}_{j^*}$. The Test~H regression coefficient on $\text{firm cost share}_{j^*} \times \mathbf{1}[\text{Post}]$, with $\text{share top}$ in percentage points, satisfies
\begin{equation}
    \beta \;\approx\; 100 \cdot \rho \cdot s_{j^*}\,(1 - \sigma)\,(1 - s_{j^*}),
    \qquad
    \sigma \;=\; 1 \;-\; \frac{\beta}{100\,\rho\,s_{j^*}\,(1 - s_{j^*})},
    \label{eq:sigma_within}
\end{equation}
where $\rho \in [0, 1]$ is the pass-through coefficient from supplier marginal cost to invoice price.

\paragraph{Within-NACE-4d bound.} Plugging in the most-favorable subset of Test~H (Q4 of the buyer's pre-shock NACE-4d expenditure share, where the supplier-level price change converts to the largest dollar shock at the buyer's total-cost level): $\widehat{\beta} = +0.03$, 95\% CI $\approx [-2.7, +2.8]$ percentage points per unit of cost-share intensity. With $s_{j^*} = 0.30$ (a representative pre-shock share for the most-exposed ETS supplier in cells with $\geq 2$ suppliers) and $\rho = 1$ (full pass-through, the upper bound on the price signal),
\[
    \sigma \;\in\; [0.87,\; 1.13]\quad(95\%\text{ CI}),\qquad
    \widehat{\sigma}\;\approx\;1.0.
\]
With $\rho = 0.5$ (a conservative lower bound on Phase~III/IV pass-through, consistent with the CMdG-tight Phase~2 estimate after sector trends), the bound widens to $\sigma \in [0.74, 1.26]$. The full sample ($\widehat{\beta} = +1.34$, s.e.\ $0.96$ on the firm-cost-share regressor) is even tighter: $\sigma \in [0.85, 1.03]$ at $\rho = 1$.

The implication is sharp. We can rule out, at conventional confidence levels, elasticities of substitution between regulated and unregulated suppliers within the same NACE 4-digit \emph{above $\sim$1.3} (under conservative pass-through assumptions) or \emph{above $\sim$1.1} (under full pass-through). The point estimates cluster around $\sigma = 1$, the Cobb--Douglas case where buyers do not reallocate at all in response to a relative-price change. Our null is consistent with $\sigma$ in a narrow neighborhood of unity. Trade-elasticity magnitudes commonly identified in import-substitution work \citep[e.g.,][with $\sigma \approx 4$]{peter2023} are outside our 95\% confidence interval.

\paragraph{Across-NACE-4d bound.} The Test~I.3 binary regulated $\times$ \textit{Post} coefficient is $\widehat{\beta} = -0.003$ (s.e.\ $0.009$, p = 0.76), with the outcome a buyer-category expenditure share. Under the across-category CES analog of \eqref{eq:sigma_within} with $\sigma_{\text{cat}}$ as the across-category elasticity, an average regulated-category pre-shock share $s_{\text{reg}} \approx 0.05$, and an average post-2015 regulated-vs-unregulated log-price differential of $\Delta \log p \approx 0.10$ (the average of CMdG-tight Phase~2 and Phase~4 coefficients with sector trends, \S\ref{sec:passthrough}),
\[
    \sigma_{\text{cat}} \;\in\; [0.5,\; 5.0]\quad(95\%\text{ CI}),\qquad
    \widehat{\sigma}_{\text{cat}}\;\approx\;1.05.
\]
This is a wider bound than the within-NACE-4d bound because the price increment is more dispersed and the average within-buyer regulated-category share is smaller. The point estimate is again near $\sigma = 1$. The bound is consistent with sector-input elasticities typically estimated in macro production-network work \citep[e.g.,][]{baqaee2019} and rules out only large elasticities.

\paragraph{Joint reading.} An honest summary is that our two reallocation margins jointly support an elasticity of substitution centered close to 1.0 with the within-NACE-4d bound the tighter of the two. Elasticities between roughly $0.85$ and $1.15$ are within the within-NACE-4d 95\% CI; elasticities up to $\sim$5 are within the across-category 95\% CI. We cannot rule out elasticities below 1 (\ie complementarity rather than substitution); we can rule out elasticities at the magnitudes typically estimated in import-substitution work for differentiated intermediates.

\subsection{Why might the elasticity be small? Five candidate explanations}

Our null at $\sigma \approx 1$ does not point uniquely at a single mechanism. Five candidate explanations are observationally consistent with the pattern; they are not mutually exclusive, and we cannot separately identify them with current data. We list them in order of how directly the data speaks to each.

\paragraph{(1) The shock is small at the typical buyer; non-linearity at the right tail is not detected.} The pair-shock-total distribution at the buyer-total-cost level is heavy-tailed. The population p99 is $\approx 39\%$ (with cement at p99 $\approx 67\%$); the population p50 is $\approx 0.002\%$. Most buyers face essentially no shock to substitute against, and the population-level null partly reflects this. \emph{However}, the right tail is informative: at p99 cells, the per-supplier price shock under full pass-through is comparable to or larger than the per-HS-product tariff cuts that \citet{peter2023} use to identify $\sigma \approx 4$ on Indian intermediates. We test the right tail directly via the Q4 pair-exposure split and find a coefficient of $+29$ pp/(unit pair-exposure) (s.e.\ $20.7$, $p = 0.16$) --- wrong-signed for substitution and not significant. A strong-non-linearity explanation in which substitution kicks in only above some threshold would predict a sharply negative Q4 coefficient with a non-trivial gap relative to Q1--Q3; we do not observe this. The data is consistent with $\sigma \approx 1$ at both modest and right-tail magnitudes; we do not detect a kink.

The honest version of the shock-magnitude story is therefore narrower: the population-level effect is small partly because most buyers face near-zero exposure, but at the right tail where the shock is large enough to identify substitution under \citet{peter2023}'s assumptions, we still do not detect substitution. We can rule out a strong threshold non-linearity at the right tail; we cannot rule out a smoother non-linearity that would only become detectable at carbon prices several multiples above the realized 2022 EUA.

\paragraph{(2) Relational capital is high in Belgian B2B.} Belgian firm-to-firm relationships are unusually persistent. Among all active pairs in 2005--2022, pairs older than five years are 18\% of pairs but $\sim$79\% of total trade. Within total-duration cohorts, mean log corrected-sales rises monotonically with pair age, and the break-up hazard falls from $\sim$46\% at age 0 to $\sim$14\% at age 18. This is a relational-capital pattern of the kind documented in \citet{baqaee2019} for production networks more broadly: the buyer-supplier match accumulates value over time (specifications, joint testing, customized billing and logistics), and switching costs grow with pair age. Substitution that requires breaking such pairs would be costly even at non-trivial relative-price increments. We do not separately identify the magnitude of these switching costs; the relational-capital pattern is consistent with $\sigma \approx 1$ within the existing pair distribution but cannot pin down whether $\sigma$ is small in a hypothetical pool of identical varieties.

\paragraph{(3) Regulated and unregulated alternatives often coincide within the same NACE 4-digit.} The within-NACE-4d substitution test requires that buyers can reach an unregulated alternative within the same supplier sector. In Belgium, ETS coverage is concentrated in heavy industries where most large suppliers in the same NACE 4-digit are themselves ETS-regulated. In NACE 19 (refined petroleum), the ETS share of revenue is essentially 100\%; in NACE 24 (basic metals), $\sim$90\%; in NACE 23 (cement and other non-metallic minerals), $\sim$58--80\%. A buyer who substitutes from an ETS cement producer to ``the alternative'' supplier in the same 4-digit category is, in many cases, substituting toward another ETS-regulated firm that absorbs the same cost shock. The relative-price gap inside the regulated NACE 4-digit is therefore much smaller than the gross supplier-level price increment, even under full pass-through. This narrows the substitution that the buyer would observe and is consistent with the within-NACE-4d null. The across-NACE-4d test (Section~\ref{sec:test_i}) is robust to this concern by construction --- it compares regulated to unregulated categories rather than within-category alternatives --- and also returns a null.

\paragraph{(4) Pass-through of carbon costs into supplier invoice prices is incomplete.} The bounds in \S\ref{sec:bounds} treat $\rho \in [0.5, 1]$ as the pass-through range. The CMdG-tight Phase~2 coefficient with sector-specific linear trends is $+0.094$ (a 9.4\% relative-PPI gap accumulated over a five-year window). If marginal-cost pass-through is partial --- because suppliers absorb part of the shock or because pass-through is delayed --- the buyer-side relative-price signal is dampened. Our $\sigma$ bound widens but does not become uninformative under partial pass-through; it does, however, reduce the buyer's incentive to substitute. The OLS pass-through evidence in \S\ref{sec:passthrough} (S6 with sector trends, $+0.07$ insignificant) and \citet{martin2014}'s Belgian firm-level finding of $+0.14$ insignificant on PRODCOM unit prices both suggest that within-sector firm-level pass-through is heterogeneous and not always close to unity.

\paragraph{(5) Buyer-side pass-through dampens the substitution incentive.} The Belgian buyers in our sample sell on to their own customers, who may absorb part of the carbon-driven cost increase. A buyer that can pass the shock downstream has a smaller incentive to bear the search and switching costs of finding an alternative supplier. We do not measure buyer-side pass-through directly; the customs evidence on cross-border substitution (a complementary analysis on the same Belgian panel, not reported here) is a null on imports from less-regulated origins, consistent with buyer-side absorption of the cost shock rather than substitution toward foreign suppliers. Mechanism (5) is the least directly testable on our data and we list it for completeness.

\paragraph{Mechanisms we cannot separate.} (1)--(2) and (3)--(4) operate jointly: a small shock at the typical buyer compounds with high relational capital, limited unregulated alternatives within the supplier sector, and partial pass-through that dampens the relative-price signal. We do not have an exclusion restriction that separates these mechanisms cleanly. The most we can say is that the joint null at $\sigma \approx 1$ is consistent with all five operating in the same direction and that the data does not single out any one as dominant.

\subsection{Selection}

The pre-shock cost-share intensity in equation~\eqref{eq:fcs} is computed from data ending in 2014 or 2016, so the regressor cannot mechanically incorporate post-2015 outcomes. There are two related selection concerns.

First, panel attrition in the GK decomposition: the fixed-base panel shrinks from 162 firms in 2005 to 100 firms in 2022, because Annual Accounts coverage is not perfectly stable. We address this with the year-on-year chained version (which uses the largest balanced subsample at each step) and the six-channel pairwise decomposition (which explicitly accounts for entry and exit). The within-sector reallocation finding survives both.

Second, the universe of buyers in Test~I excludes buyers with no positive pre-shock spending in the category. This exclusion is needed to define the buyer-category cell, but it means the test has no power against substitution that operates by a buyer adding a new category to its input bill. We do not have a direct test for this margin and flag it as a gap in coverage rather than an estimated null.

\subsection{External validity}

Belgium is a small open economy and the Belgian ETS is a small subset of the EU-wide system. Three external validity concerns deserve flagging:

\begin{enumerate}
    \item \emph{ETS firms in Belgium are large and established.} The 281 EUTL installations are concentrated in established firms (steel, cement, refining, primary chemicals), all of which were operating throughout the sample window. The composition of the regulated set is older and more capital-intensive than the average EU ETS sector. A test in a setting with more entry of new regulated firms --- or more exit of old ones --- might find different reallocation magnitudes.

    \item \emph{The 2017--2022 EUA price path is one realization of one policy.} Our identification leans on the post-2017 MSR-driven price rise. Different prices, different time horizons, or different cap stringencies might produce different reallocation responses. We do not extrapolate.

    \item \emph{Belgium's B2B network is unusually well-measured.} The near-universal NBB B2B records make this a high-power setting for observational substitution tests; settings without similar firm-to-firm coverage may not be able to replicate this specification at all. The applicability of our null to settings without similar data is unclear.
\end{enumerate}

We do not claim that our null is a universal result. We claim that, for Belgian buyers facing the post-2017 EU ETS price increment, on the two margins we observe, the data put a tight bound on the elasticity of substitution centered close to unity and rule out the large reallocation that the leakage hypothesis predicts.
