The elasticity of substitution between carbon-regulated and unregulated suppliers is the central parameter governing the reallocation response to a unilateral carbon price. In standard production-network models of carbon policy \citep[e.g.,][]{baqaee2019,king2019,aghion2024}, the size and sign of the reallocation channel that determines how much aggregate emissions move in response to a targeted carbon tax is proportional to this elasticity. Yet there is no direct firm-level estimate of it. Trade-elasticity work for differentiated intermediates returns values around $\sigma \approx 4$ \citep[e.g.,][]{peter2023}; macro production-network calibrations are routinely set near unity \citep{baqaee2019}; and the difference is the difference between very large and very small carbon-policy reallocation effects. This paper estimates $\sigma$ directly, using the post-2017 EU ETS price increment as the cost shock to regulated suppliers and Belgian firm-to-firm transactions as the buyer-response panel.

Our estimation has two empirical preconditions. First, carbon costs must \emph{pass through} into the prices buyers pay; otherwise the relative-price signal a buyer sees is muted relative to the supplier's marginal cost. Second, conditional on pass-through, buyers must reweight their input mix --- and the rate at which they do so is what identifies $\sigma$. We document supplier-side pass-through in our Belgian panel: a monthly panel local projection on the structural carbon-policy shock returns a peak PPI response of $+4.08$ (s.e.\ $0.64$) at 12 months, and a regulated-vs-unregulated event study with sector-specific linear trends returns differential PPI gaps of $+0.094$ in Phase~2 and $+0.113$ in Phase~4 (\S\ref{sec:passthrough}). We take the pass-through evidence as supporting a price signal in the range $\rho \in [0.5, 1]$ and report bounds on $\sigma$ under both endpoints.

We then estimate buyer-side reallocation using Belgian firm-to-firm transaction records. The Belgian setting is well-suited to this question for three reasons. First, the National Bank of Belgium maintains a near-universal panel of business-to-business invoices linked by VAT identifier; we observe the full domestic supplier composition of essentially every Belgian buyer. Second, ETS-regulated installations are a small but identifiable subset of suppliers ($\sim$280 firms, concentrated in a handful of NACE 2-digit sectors) for which we can measure pre-shock carbon-cost intensity using EUTL allowance and emissions records merged with Annual Accounts revenues. Third, the EU ETS supplies a pre-specified policy event with a well-understood discontinuity in policy stringency: the 2017 Market Stability Reserve reform triggered a roughly tenfold rise in EUA prices over 2017--2022, generating a Phase~IV cost shock with order-of-magnitude variation in pair-level pass-through exposure.

We examine reallocation at two margins. The first --- within a narrowly defined supplier sector (NACE 4-digit), \emph{across suppliers} --- corresponds to the substitution a buyer can make without changing the composition of its input basket. The second --- \emph{across} NACE 4-digit input categories within the same buyer-year --- corresponds to the substitution a buyer can make by reweighting categories of inputs (\eg substituting away from cement toward steel) when the average price in one category rises relative to others.

\paragraph{Findings.} Mapped into a CES nest, both margins identify $\sigma$ in a tight neighborhood of unity. The reduced-form regression coefficients themselves are statistically indistinguishable from zero under specifications closest to current best practice for difference-in-differences with continuous and binary treatments, two-way clustered standard errors, and high-dimensional fixed effects --- which, in CES space, is precisely what places $\sigma$ at the Cobb-Douglas point with tight precision:

\begin{itemize}
    \item \textbf{Within-NACE-4d, across-supplier substitution.} The headline pair-exposure regression on 14{,}450 buyer $\times$ NACE-4d cells gives a pooled coefficient of $-16.7$ (s.e.\ $17.4$, $p = 0.34$); a specification that adds a 2005--2014 linear-trend control returns $+5.4$ (s.e.\ $20.4$, $p = 0.79$), with the trend coefficient itself not statistically distinguishable from zero ($p = 0.42$). On the larger 32{,}631-cell sample using the firm-cost-share regressor, the pooled coefficient is $+1.34$ (s.e.\ $0.96$, $p = 0.16$), and the most economically-favorable subset --- cells where the supplier's NACE 4-digit accounts for the largest share of the buyer's total input bill, \ie where any per-unit price change converts to the largest dollar shock at the buyer's total-cost level --- gives $\beta = +0.03$ (s.e.\ $1.39$, $p = 0.98$).

    \item \textbf{Across-NACE-4d, across-category substitution.} On a buyer $\times$ NACE 4-digit $\times$ year panel of 71.7 million cell-years, our preferred specification --- a binary regulated-category $\times$ \textit{Post} dummy with buyer $\times$ year and buyer $\times$ NACE 4-digit fixed effects, the most direct domestic analog of the regulated/unregulated event study in \citet{colmeretal2023} --- yields $\beta = -0.003$ (s.e.\ $0.009$, $p = 0.76$). The continuous-treatment event study shows uniformly \emph{positive} year coefficients in every clean post-2015 year (2015--2019 and 2021), pointing in the opposite direction from substitution.

    \item \textbf{Bounds on the elasticity of substitution.} Mapping the within-NACE-4d Q4 coefficient to a CES elasticity, under a representative pre-shock supplier share of $0.30$ and our preferred (conservative) pass-through coefficient $\rho = 0.5$, gives a 95\% confidence interval of $\sigma \in [0.74, 1.26]$ centered at $\sigma = 1.0$. Under full pass-through ($\rho = 1$, the upper-bound-on-precision case), the interval tightens to $\sigma \in [0.87, 1.13]$. The full sample under $\rho = 1$ is even tighter, $\sigma \in [0.85, 1.03]$. The across-NACE-4d binary coefficient gives a wider but consistent bound $\sigma_{\text{cat}} \in [0.5, 5.0]$ centered at $\sigma_{\text{cat}} = 1.05$. Both margins place $\sigma$ tightly around the Cobb-Douglas benchmark and rule out, at conventional confidence levels, elasticities at the magnitudes typically estimated in import-substitution work for differentiated intermediates \citep[e.g.,][]{peter2023}.

    \item \textbf{Descriptive complement.} A standard Grossman--Krueger \citep{grossman1993} emissions decomposition on the same Belgian ETS firm panel attributes the 46\% aggregate emissions decline over 2005--2022 to scale, between-sector reallocation, within-sector reallocation, and within-firm abatement. Within-sector reallocation is essentially zero across all years and across both fixed-base and year-on-year specifications. This is consistent with --- though not equivalent to --- the buyer-side null at the within-NACE-4d margin.
\end{itemize}

\paragraph{What we do and do not claim.} The contribution of this paper is a direct, identification-disciplined estimate of the elasticity of substitution between regulated and unregulated suppliers in a setting with a sharp policy event, full-network B2B coverage, and a credible price signal. The point estimate is Cobb-Douglas; the 95\% CI is tight enough to rule out the elasticities used in import-substitution and trade-elasticity work, and wide enough to be consistent with complementarity. We do not claim that $\sigma$ is structural in the sense of being invariant across settings or carbon-price regimes: in particular, we do not claim that buyers \textit{would not} reallocate more aggressively at higher carbon prices, and we are explicit that our identification window is the post-2017 EUA price path. The data are consistent with several non-mutually-exclusive mechanisms for $\sigma \approx 1$: (i) shock magnitudes are small at the typical pair, but the right tail of pair-exposure --- where shocks are large enough to identify $\sigma \approx 4$ under \citet{peter2023}'s assumptions --- gives a coefficient that is wrong-signed for substitution and not statistically distinguishable from the pooled estimate, so this explanation has the \emph{least} direct empirical support among the five; (ii) Belgian B2B exhibits substantial relational capital --- pairs older than five years are 18\% of pairs but $\sim$79\% of total trade --- that raises switching costs; (iii) within heavily ETS-regulated NACE 4-digit categories (refining, basic metals, much of cement and chemicals), the ``unregulated alternative'' is itself often ETS-regulated, narrowing the within-sector relative-price gap; (iv) supplier-side pass-through is partial, dampening the relative-price signal that would induce buyer substitution; (v) buyer-side pass-through onto buyers' own customers further dampens the substitution incentive. We discuss each in Section~\ref{sec:discussion} and what they imply for quantitative models of carbon policy in production networks.

A small but statistically detectable extensive-margin response exists on the within-NACE-4d test: an ancillary linear probability model on whether the most-exposed supplier remains active in the buyer-cell post-2015 yields $\beta = -3.61$ (s.e.\ $1.47$, $p = 0.014$). At typical exposure (90th percentile of cost-share intensity $\approx 0.0014$), the predicted probability of the supplier exiting the relationship rises by roughly half a percentage point. The point estimate is statistically detectable; the implied magnitude is small relative to baseline relationship-exit rates. We report this as a real but economically modest qualifier on the intensive-margin null.

\paragraph{Related literature.} We connect to four strands. First, on EU ETS impacts on regulated firms: \citet{martin2014}, \citet{dechezlepretreetal2023}, \citet{colmeretal2023}, and \citet{kanzig2023unequal}. Our $\sigma \approx 1$ estimate is consistent with the literature finding that ETS firms reduced emissions without contracting output: large reallocation toward unregulated competitors (which a higher $\sigma$ would predict) would be hard to reconcile with that pattern. Second, on the elasticity of substitution between intermediate inputs in production-network calibrations: \citet{baqaee2019} and the macro literature it surveys typically work with $\sigma$ in a neighborhood of unity; our estimate provides direct firm-level micro-evidence supporting that calibration choice in the carbon-policy context. Third, on input-output reallocation under cost shocks identified in trade microdata: \citet{huneeus2018} and \citet{peter2023}, where elasticities of $\sigma \approx 4$ are typical. Our estimate is far below those values, and we discuss why in Section~\ref{sec:discussion}. Fourth, on the demand-side elasticity in environmental settings: \citet{Hsiao2026} estimates own-price palm-oil demand elasticities of $0.7$ to $0.9$ using an AIDS specification with weather IVs and emphasizes that low substitution \emph{strengthens} the case for trade-policy intervention because it limits leakage to unregulated markets. Our $\sigma$ estimate plays an analogous structural role for production-network models of carbon policy.

The remainder of the paper proceeds as follows. Section~\ref{sec:data} describes the data and sample construction and presents the pass-through evidence we use to anchor magnitudes. Section~\ref{sec:decomposition} presents the descriptive supplier-side decomposition. Section~\ref{sec:test_h} reports the within-NACE-4d test. Section~\ref{sec:test_i} reports the across-NACE-4d test. Section~\ref{sec:discussion} maps the regression coefficients to elasticity bounds and discusses candidate mechanisms. Section~\ref{sec:conclusion} concludes.
